% ============================================================
%  Open Hybrid Cloud Infrastructure Webshop — Technical Handbook
% ============================================================
\documentclass[12pt,a4paper,twoside]{report}

% ── Encoding & fonts ─────────────────────────────────────────
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}

% ── Page layout ──────────────────────────────────────────────
\usepackage[
  a4paper,
  top=30mm, bottom=30mm,
  inner=30mm, outer=25mm,
  headheight=15pt
]{geometry}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[LE]{\small\nouppercase{\leftmark}}
\fancyhead[RO]{\small\nouppercase{\rightmark}}
\fancyfoot[C]{\small\thepage}
\renewcommand{\headrulewidth}{0.4pt}

% ── Colors ───────────────────────────────────────────────────
\usepackage[dvipsnames,table]{xcolor}
\definecolor{ohc-blue}{HTML}{131921}
\definecolor{ohc-amber}{HTML}{febd69}
\definecolor{c4-person}{HTML}{08427b}
\definecolor{c4-system}{HTML}{1168bd}
\definecolor{c4-external}{HTML}{6b6b6b}
\definecolor{c4-container}{HTML}{2E7D98}
\definecolor{c4-component}{HTML}{4585A5}
\definecolor{c4-database}{HTML}{2D6A4F}
\definecolor{note-bg}{HTML}{FFF9C4}
\definecolor{warn-bg}{HTML}{FFECB3}
\definecolor{code-bg}{HTML}{F5F5F5}
\definecolor{link-color}{HTML}{1565C0}

% ── Graphics & TikZ ──────────────────────────────────────────
\usepackage{tikz}
\usetikzlibrary{shapes.geometric,shapes.multipart,arrows.meta,positioning,fit,backgrounds,calc}

\tikzset{
  c4person/.style={
    rectangle, rounded corners=8pt,
    draw=c4-person!80, fill=c4-person!15,
    text width=3.2cm, align=center,
    minimum height=2.0cm, font=\small\bfseries
  },
  c4system/.style={
    rectangle,
    draw=c4-system!80, fill=c4-system!20,
    text width=3.4cm, align=center,
    minimum height=1.8cm, font=\small\bfseries
  },
  c4external/.style={
    rectangle,
    draw=c4-external!80, fill=c4-external!15,
    text width=3.4cm, align=center,
    minimum height=1.8cm, font=\small\bfseries
  },
  c4container/.style={
    rectangle,
    draw=c4-container!80, fill=c4-container!20,
    text width=3.4cm, align=center,
    minimum height=2.0cm, font=\small\bfseries
  },
  c4database/.style={
    cylinder,
    draw=c4-database!80, fill=c4-database!20,
    shape border rotate=90,
    text width=2.8cm, align=center,
    minimum height=1.8cm, font=\small\bfseries
  },
  c4component/.style={
    rectangle,
    draw=c4-component!80, fill=c4-component!15,
    text width=3.0cm, align=center,
    minimum height=1.6cm, font=\scriptsize\bfseries
  },
  c4boundary/.style={
    dashed, draw=gray!60, fill=gray!5,
    rounded corners=4pt
  },
  c4arrow/.style={
    ->, >=Stealth[round], thick,
    draw=gray!70
  },
  c4label/.style={
    font=\scriptsize\itshape, text=gray!60!black,
    align=center
  },
  c4sublabel/.style={
    font=\tiny, text=gray!50, align=center
  },
}

% ── Tables ───────────────────────────────────────────────────
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{tabularx}
\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
\newcolumntype{C}[1]{>{\centering\arraybackslash}p{#1}}

% ── Code listings ─────────────────────────────────────────────
\usepackage{listings}
\lstset{
  backgroundcolor=\color{code-bg},
  basicstyle=\ttfamily\footnotesize,
  breaklines=true,
  breakatwhitespace=false,
  postbreak=\mbox{\textcolor{gray}{$\hookrightarrow$}\enspace},
  frame=single,
  framesep=4pt,
  rulecolor=\color{gray!40},
  tabsize=2,
  showstringspaces=false,
  captionpos=b,
  xleftmargin=6pt,
  xrightmargin=6pt,
  columns=flexible,
}
\lstdefinestyle{bash}{
  language=bash,
  keywordstyle=\color{MidnightBlue}\bfseries,
  commentstyle=\color{gray},
  stringstyle=\color{ForestGreen},
}
\lstdefinestyle{go}{
  language=Go,
  keywordstyle=\color{MidnightBlue}\bfseries,
  commentstyle=\color{gray},
  stringstyle=\color{ForestGreen},
}
\lstdefinestyle{hcl}{
  morekeywords={resource,variable,output,module,provider,terraform,
                required_providers,backend,locals,data,for_each,
                dynamic,content,default,type,description,value,source,
                required_version,sensitive},
  keywordstyle=\color{MidnightBlue}\bfseries,
  commentstyle=\color{gray},
  stringstyle=\color{ForestGreen},
}
\lstdefinestyle{yaml}{
  language=,
  morekeywords={true,false,null},
  keywordstyle=\color{MidnightBlue},
  commentstyle=\color{gray},
  stringstyle=\color{ForestGreen},
}
\lstdefinestyle{sql}{
  language=SQL,
  keywordstyle=\color{MidnightBlue}\bfseries,
  commentstyle=\color{gray},
  stringstyle=\color{ForestGreen},
}

% ── Callout boxes ─────────────────────────────────────────────
\usepackage[most]{tcolorbox}
\tcbset{
  noteboxstyle/.style={
    colback=note-bg, colframe=Goldenrod!80!black,
    fonttitle=\bfseries, title={Note},
    left=4pt, right=4pt, top=4pt, bottom=4pt,
    boxrule=0.8pt
  },
  warnboxstyle/.style={
    colback=warn-bg, colframe=Orange!80!black,
    fonttitle=\bfseries, title={Important},
    left=4pt, right=4pt, top=4pt, bottom=4pt,
    boxrule=0.8pt
  },
  tipboxstyle/.style={
    colback=green!8, colframe=ForestGreen!70,
    fonttitle=\bfseries, title={Tip},
    left=4pt, right=4pt, top=4pt, bottom=4pt,
    boxrule=0.8pt
  },
}
\newcommand{\notebox}[1]{\begin{tcolorbox}[noteboxstyle]#1\end{tcolorbox}}
\newcommand{\warnbox}[1]{\begin{tcolorbox}[warnboxstyle]#1\end{tcolorbox}}
\newcommand{\tipbox}[1]{\begin{tcolorbox}[tipboxstyle]#1\end{tcolorbox}}

% ── Misc packages ─────────────────────────────────────────────
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage{float}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{pdflscape}
\usepackage{amsmath}
\usepackage{pifont}
% xurl extends hyperref's \url to allow line breaks at more characters
\usepackage{xurl}
% Allow generous inter-word spacing to prevent overfull hboxes in text
\setlength{\emergencystretch}{3em}
\newcommand{\cmark}{\ding{51}}
\newcommand{\xmark}{\ding{55}}

% ── Hyperlinks ────────────────────────────────────────────────
\usepackage[
  colorlinks=true,
  linkcolor=link-color,
  urlcolor=link-color,
  citecolor=link-color,
  pdfauthor={Open Hybrid Cloud Infrastructure Team},
  pdftitle={Open Hybrid Cloud Infrastructure Webshop — Technical Handbook},
  pdfsubject={Technical documentation for administrators, developers, and project managers},
  pdfkeywords={Open Hybrid Cloud, webshop, infrastructure, OpenTofu, GitLab, Linode, Go, C4},
  bookmarksnumbered=true,
  hypertexnames=true,
  unicode=true,
]{hyperref}

% ── Chapter style ─────────────────────────────────────────────
\usepackage{titlesec}
\titleformat{\chapter}[display]
  {\normalfont\huge\bfseries\color{ohc-blue}}
  {\chaptertitlename\ \thechapter}{12pt}{\Huge}
\titleformat{\section}
  {\normalfont\Large\bfseries\color{ohc-blue!80}}
  {\thesection}{1em}{}
\titleformat{\subsection}
  {\normalfont\large\bfseries\color{ohc-blue!60}}
  {\thesubsection}{1em}{}

% ── Custom commands ───────────────────────────────────────────
\newcommand{\code}[1]{\texttt{#1}}
\newcommand{\file}[1]{\texttt{\textcolor{MidnightBlue}{#1}}}
\newcommand{\term}[1]{\textit{#1}}
\newcommand{\route}[1]{\texttt{\textcolor{ForestGreen}{#1}}}
\newcommand{\env}[1]{\texttt{\textcolor{Maroon}{#1}}}
\newcommand{\role}[1]{\textsf{\textbf{#1}}}

% ── Version info ──────────────────────────────────────────────
\newcommand{\docversion}{1.1}
\newcommand{\docdate}{\today}

% ─────────────────────────────────────────────────────────────
\begin{document}

% ── Title page ───────────────────────────────────────────────
\begin{titlepage}
  \begin{tikzpicture}[remember picture, overlay]
    \fill[ohc-blue] (current page.north west) rectangle
      ([yshift=-5cm] current page.north east);
    \fill[ohc-amber] ([yshift=-5cm] current page.north west) rectangle
      ([yshift=-5.4cm] current page.north east);
  \end{tikzpicture}

  \vspace*{2.5cm}

  {\color{white}\fontsize{28}{34}\selectfont\bfseries
    Open Hybrid Cloud\\[6pt]
    Infrastructure Webshop}

  \vspace{2.2cm}

  {\fontsize{22}{28}\selectfont\bfseries Technical Handbook}

  \vspace{0.4cm}
  {\large\color{gray!60!black} Version \docversion\ · \docdate}

  \vfill

  \begin{tabular}{@{}ll}
    \toprule
    \textbf{Autor}     & Maximilian Jakob Maag B.Sc. \\
    \textbf{Audience}  & Administrators, Developers, Project Managers \\
    \textbf{System}    & Infrastructure Webshop \\
    \textbf{Stack}     & Go · PostgreSQL · HTMX · OpenTofu · GitLab · Linode \\
    \textbf{Scope}     & Architecture · Operations · Development · Product Lifecycle \\
    \bottomrule
  \end{tabular}

  \vspace{1cm}
  {\small\color{gray}Open Hybrid Cloud — Digital Unit Infrastructure Team}
\end{titlepage}

% ── Front matter ─────────────────────────────────────────────
\tableofcontents
\listoffigures
\listoftables
\lstlistoflistings

% ─────────────────────────────────────────────────────────────
%  PART I — OVERVIEW & ARCHITECTURE
% ─────────────────────────────────────────────────────────────
\part{Overview \& Architecture}
\label{part:arch}

% ─────────────────────────────────────────────────────────────
\chapter{Introduction}
\label{ch:intro}

\section{Purpose of This Handbook}

Open Hybrid Cloud is an open-source, self-service portal that enables Admins and Project Managers to order, manage, and decommission IT infrastructure on Linode/Akamai Cloud through a browser-based interface. The source code is publicly available at \url{https://github.com/Maximilian-Maag/open-hybrid-cloud}. This handbook is the authoritative reference for everyone who operates, extends, or uses the system.

It covers:
\begin{itemize}
  \item The complete system architecture described with the C4 model
  \item Infrastructure-as-Code modules and the GitLab CI/CD concept
  \item Architecture and design decisions with their rationale
  \item Step-by-step administrator operations
  \item Developer onboarding, code structure, and extension patterns
  \item The full product lifecycle from creation to decommissioning
\end{itemize}

\section{Target Audiences}

\begin{description}[leftmargin=3.5cm, style=nextline]
  \item[\role{Admin}]
    Responsible for approving orders, monitoring all infrastructure, and
    ordering directly without an approval step. Reads
    Part~\ref{part:admin} and Part~\ref{part:pm}.
  \item[\role{Root}]
    Responsible for the product catalog, system configuration, and local
    user accounts. Reads Part~\ref{part:admin} entirely.
  \item[\role{Developer}]
    Extends or maintains the webshop codebase and the OpenTofu modules.
    Reads Part~\ref{part:arch} and Part~\ref{part:dev}.
  \item[\role{Project Manager}]
    Places infrastructure orders and manages projects. Reads
    Part~\ref{part:pm}.
\end{description}

\section{Conventions Used in This Handbook}

\begin{description}
  \item[\code{monospace}] File paths, commands, code, environment variables, and route patterns.
  \item[\textit{italic}] Technical terms on first use.
  \item[\textbf{bold}] UI labels, button names, and menu items.
  \item[Note boxes] Yellow-highlighted boxes providing additional context or important background information.
  \item[Important boxes] Orange-highlighted boxes warning about actions that can cause data loss or service disruption.
  \item[Tip boxes] Green-highlighted boxes with shortcuts and best practices.
\end{description}

\section{System At a Glance}

The webshop is a Next.js monorepo with a dedicated backend API and a
React-based frontend. Orders are fulfilled by triggering CI/CD pipelines
(GitLab, GitHub, or Bitbucket) that run OpenTofu (a
Terraform-compatible open-source tool) to provision or destroy cloud
resources on Linode/Akamai. Pipeline status is reported back via
webhooks rather than polling.

\begin{table}[H]
  \centering
  \caption{Technology stack overview}
  \label{tab:stack}
  \begin{tabularx}{\linewidth}{@{}l>{\raggedright\arraybackslash}Xl@{}}
    \toprule
    \textbf{Layer} & \textbf{Technology} & \textbf{Version} \\
    \midrule
    Runtime        & Node.js                  & 22+ \\
    Backend        & Next.js 15 (API-only)    & 15.x \\
    Frontend       & Next.js 15 + React       & 15.x / 19.x \\
    CSS            & Tailwind CSS v4          & 4.x \\
    Package Mgr    & pnpm (workspace)         & 9.x \\
    ORM            & Drizzle ORM              & — \\
    Database       & PostgreSQL               & 15+ \\
    Auth (backend) & JWT HS256 (jose)         & 24 h expiry \\
    Auth (frontend)& NextAuth v5              & 5.x \\
    IaC            & OpenTofu                 & 1.9+ \\
    Cloud          & Linode/Akamai            & — \\
    CI/CD          & GitLab / GitHub / Bitbucket & 16+ / — / — \\
    State Backend  & GitLab Managed TF State  & — \\
    \bottomrule
  \end{tabularx}
\end{table}

% ─────────────────────────────────────────────────────────────
\chapter{C4 Architecture Model}
\label{ch:c4}

The system is described using the \term{C4 model} (Context, Container,
Component, Code). Each level zooms in one step deeper.

% ── Level 1 ──────────────────────────────────────────────────
\section{Level 1 — System Context}
\label{sec:c4-l1}

Figure~\ref{fig:c4-l1} shows who uses the webshop and which external
systems it depends on.

\begin{figure}[H]
\centering
\resizebox{\textwidth}{!}{%
\begin{tikzpicture}[node distance=1.0cm and 1.2cm]

  % Central system
  \node[c4system, text width=4cm, minimum height=2.4cm] (ws)
    {\textbf{Open Hybrid Cloud}\\[4pt]
     \scriptsize Self-service portal for ordering, managing and decommissioning IT infrastructure.\\
     \scriptsize Next.js · React · PostgreSQL};

  % Persons (top)
  \node[c4person, above left=1.8cm and 2.6cm of ws] (dua)
    {\textbf{Admin}\\[4pt]\scriptsize Orders directly, approves/rejects, sees all infrastructure};
  \node[c4person, above=1.8cm of ws] (sa)
    {\textbf{Root}\\[4pt]\scriptsize Manages catalog \& config};
  \node[c4person, above right=1.8cm and 2.6cm of ws] (pl)
    {\textbf{Project Manager}\\[4pt]\scriptsize Orders own infrastructure};

  % External systems (bottom row)
  \node[c4external, below left=2.0cm and 4.0cm of ws] (gl)
    {\textbf{CI Provider}\\[4pt]\scriptsize GitLab / GitHub / Bitbucket — webhook target, repo browser};
  \node[c4external, below right=2.0cm and 0.8cm of ws] (er)
    {\textbf{Exchange Rate API}\\[4pt]\scriptsize Currency conversion rates (optional)};
  \node[c4external, below right=2.0cm and 4.0cm of ws] (smtp)
    {\textbf{Mail Server}\\[4pt]\scriptsize SMTP transactional email};

  % Arrows — persons to webshop
  \draw[c4arrow] (dua)  -- node[c4label, right=1pt]{Uses HTTPS} (ws);
  \draw[c4arrow] (sa)   -- node[c4label, right=1pt]{Uses HTTPS} (ws);
  \draw[c4arrow] (pl)   -- node[c4label, right=1pt]{Uses HTTPS} (ws);

  % Arrows — webshop to external
  \draw[c4arrow] (ws) -- node[c4label, left=1pt, align=right]
    {Webhooks, API\\JSON/HTTPS} (gl);
  \draw[c4arrow] (ws) -- node[c4label, right=1pt]{JSON/HTTPS} (er);
  \draw[c4arrow] (ws) -- node[c4label, right=1pt]{SMTP} (smtp);

\end{tikzpicture}}%
\caption{C4 Level 1 — System Context Diagram}
\label{fig:c4-l1}
\end{figure}

\subsection{Actors}

\begin{description}
  \item[\role{Admin}]
    Authenticates via local account with JWT. Has the system role
    \code{admin}. Can order infrastructure directly (no approval required),
    approve or reject orders from Project Managers, view all projects and
    infrastructure, and decommission any resource.
  \item[\role{Root}]
    Uses a local account. Has the system role \code{root}.
    Manages the product catalog, system configuration (SMTP, branding,
    currencies), environments, CI sources, cost centers, and local
    users. Cannot place orders.
  \item[\role{Project Manager}]
    Authenticates via local account with JWT. Has the system role
    \code{project\_manager}. Places orders (which require Admin
    approval), manages their own projects, and can decommission their
    own infrastructure.
\end{description}

\subsection{External Systems}

\begin{description}
  \item[\textbf{CI Provider (GitLab / GitHub / Bitbucket)}]
    One or more self-hosted or cloud CI provider instances. The webshop
    connects for two purposes: (1) browsing repositories and importing
    \code{variables.tf} parameter definitions via the GitLab API, and
    (2) triggering provisioning and decommissioning webhooks. Pipeline
    status is reported back to the webshop via inbound webhook events
    (\route{POST /api/webhooks/\{provider\}/pipeline}).
  \item[\textbf{Exchange Rate API}]
    Optional. Any HTTP JSON exchange rate endpoint. Used to refresh
    currency conversion rates. Configured via
    \env{EXCHANGE\_RATE\_API\_URL} and \env{EXCHANGE\_RATE\_API\_KEY}.
  \item[\textbf{Mail Server}]
    Any SMTP server. Sends order confirmations, approval request
    notifications, approval/rejection notices, deployment completion
    alerts, and failure notifications. Delivered via nodemailer.
\end{description}

% ── Level 2 ──────────────────────────────────────────────────
\section{Level 2 — Container Diagram}
\label{sec:c4-l2}

\begin{figure}[H]
\centering
\begin{tikzpicture}[node distance=1.4cm and 1.8cm]

  % System boundary
  \begin{scope}[on background layer]
    \node[c4boundary, fit={(-0.5,-0.5)(12,6.5)}, inner sep=0.6cm,
          label={[font=\small\itshape]above left:Open Hybrid Cloud System}] (bound) {};
  \end{scope}

  % Frontend container
  \node[c4container, text width=3.6cm, minimum height=3.0cm] (fe) at (2,3)
    {\textbf{Frontend}\\[4pt]
     \scriptsize React UI, App Router pages,\\
     NextAuth v5 session,\\
     typed API client.\\[4pt]
     \scriptsize\textit{Next.js 15 · React 19 · :3000}};

  % Backend container
  \node[c4container, text width=3.6cm, minimum height=3.0cm] (be) at (7,3)
    {\textbf{Backend API}\\[4pt]
     \scriptsize REST route handlers,\\
     JWT auth middleware,\\
     Drizzle ORM, webhooks,\\
     notifications.\\[4pt]
     \scriptsize\textit{Next.js 15 · Node.js 22 · :3001}};

  % Database
  \node[c4database, right=2.2cm of be] (db)
    {\textbf{PostgreSQL}\\[4pt]
     \scriptsize All persistent data};

  % Persons (above)
  \node[c4person, above left=1.6cm and 0.4cm of fe] (dua)
    {\textbf{Admin}};
  \node[c4person, above=1.6cm of fe] (sa)
    {\textbf{Root}};
  \node[c4person, above right=1.6cm and 0.4cm of fe] (pl)
    {\textbf{Project Manager}};

  % External below
  \node[c4external, below left=1.6cm and 0.5cm of be, text width=2.8cm] (ci)
    {\textbf{CI Provider}};
  \node[c4external, below right=1.6cm and 0.5cm of be, text width=2.8cm] (smtp)
    {\textbf{SMTP}};

  % Arrows
  \draw[c4arrow] (dua) -- (fe);
  \draw[c4arrow] (sa)  -- (fe);
  \draw[c4arrow] (pl)  -- (fe);
  \draw[c4arrow] (fe) -- node[c4label,above]{REST/HTTPS} (be);
  \draw[c4arrow] (be) -- node[c4label,above]{Drizzle/TCP} (db);
  \draw[c4arrow] (be) -- node[c4label,right=2pt]{JSON/HTTPS} (ci);
  \draw[c4arrow] (be) -- node[c4label,right=2pt]{SMTP} (smtp);

\end{tikzpicture}
\caption{C4 Level 2 — Container Diagram}
\label{fig:c4-l2}
\end{figure}

The system has three containers (plus the shared database):

\begin{description}
  \item[\textbf{Frontend} (port 3000)]
    A Next.js 15 application serving the React UI via the App Router.
    All pages are React Server Components or client components. It
    communicates with the backend exclusively via typed fetch wrappers
    in \file{src/lib/api.ts}. Authentication state is managed by
    NextAuth v5, which stores the JWT received from the backend in a
    secure server-side session.
  \item[\textbf{Backend API} (port 3001)]
    A Next.js 15 application running in API-only mode — no UI pages.
    Route handlers under \file{src/app/api/} expose the full REST
    surface. JWT middleware (\file{src/lib/auth/}) verifies every
    authenticated request. Drizzle ORM manages all database access.
    The webhook handler (\file{src/lib/webhook/}) processes inbound
    pipeline status events from CI providers.
  \item[\textbf{PostgreSQL Database}]
    The single source of truth. Stores the product catalog, orders,
    infrastructure state, audit log, branding, configuration, users, and
    exchange rates. The database is the only stateful component.
\end{description}

% ── Level 3 ──────────────────────────────────────────────────
\section{Level 3 — Component Diagram}
\label{sec:c4-l3}

Figure~\ref{fig:c4-l3} decomposes the backend API container into
its major logical components.

\begin{figure}[H]
\centering
\resizebox{\textwidth}{!}{%
\begin{tikzpicture}[node distance=0.7cm and 0.6cm]

  % Top row — route handler groups
  \node[c4component] (auth)
    {\textbf{Auth Routes}\\[2pt]\scriptsize login, me, logout};
  \node[c4component, right=of auth] (catalog)
    {\textbf{Catalog Routes}\\[2pt]\scriptsize Products, categories, pricing};
  \node[c4component, right=of catalog] (order)
    {\textbf{Order Routes}\\[2pt]\scriptsize Place, approve, reject};
  \node[c4component, right=of order] (infra)
    {\textbf{Infrastructure Routes}\\[2pt]\scriptsize Overview, decommission};
  \node[c4component, right=of infra] (admin)
    {\textbf{Admin Routes}\\[2pt]\scriptsize Catalog \& config mgmt};

  % Middle row — lib modules
  \node[c4component, below=0.9cm of auth] (jwtmw)
    {\textbf{JWT Middleware}\\[2pt]\scriptsize Verify token, role guards};
  \node[c4component, right=of jwtmw] (ci)
    {\textbf{CI Dispatch}\\[2pt]\scriptsize GitLab/GitHub/Bitbucket};
  \node[c4component, right=of ci] (webhook)
    {\textbf{Webhook Handler}\\[2pt]\scriptsize Inbound pipeline events};
  \node[c4component, right=of webhook] (email)
    {\textbf{Email}\\[2pt]\scriptsize nodemailer SMTP};
  \node[c4component, right=of email] (bootstrap)
    {\textbf{Bootstrap}\\[2pt]\scriptsize Root user seed};

  % Bottom row — data layer
  \node[c4database, below=0.9cm of jwtmw, text width=2.8cm] (drizzle)
    {\textbf{Drizzle ORM}\\[2pt]\scriptsize Schema + typed queries};

  % Arrows: components to drizzle
  \foreach \n in {auth, catalog, order, infra, admin, jwtmw, ci, webhook, email, bootstrap}
    \draw[->, thick, draw=gray!40, dashed] (\n) -- (drizzle);

\end{tikzpicture}
}
\caption{C4 Level 3 — Component Diagram (Backend API)}
\label{fig:c4-l3}
\end{figure}

\subsection{Component Descriptions}

\begin{longtable}{@{}L{3.0cm}L{10cm}@{}}
  \toprule
  \textbf{Component} & \textbf{Responsibility} \\
  \midrule
  \endhead
  Auth Routes &
    \route{POST /api/auth/login} validates credentials with bcryptjs,
    issues a signed HS256 JWT (24 h). \route{GET /api/auth/me} returns
    the caller's profile. \route{POST /api/auth/logout} is a stateless
    no-op (JWT expiry handles invalidation). \\[4pt]
  Catalog Routes &
    Returns products grouped by category (\route{GET /api/catalog}).
    Converts prices using stored exchange rates. \\[4pt]
  Order Routes &
    \route{POST /api/catalog/:id/order} creates an order and dispatches
    the CI webhook immediately for Admins, or parks it for approval for
    Project Managers. \route{POST /api/orders/:id/approve} and
    \route{POST /api/orders/:id/reject} complete the approval flow with
    email notifications and audit writes. \\[4pt]
  Infrastructure Routes &
    Shows deployed resources role-scoped by caller. Triggers the CI
    destroy webhook for decommissioning. Supports ``use as template''
    to pre-fill a new order. \\[4pt]
  Admin Routes &
    All Root-only pages: categories, products (CRUD, image upload,
    webhook management, parameter import from \code{variables.tf} via
    GitLab API), environments, CI sources, cost centers, currencies,
    SMTP config, branding, users. \\[4pt]
  JWT Middleware &
    Verifies Bearer tokens on every authenticated route using the
    \code{jose} library. Exports typed role guard wrappers
    (\code{requireAdmin}, \code{requireRoot}) used by route handlers. \\[4pt]
  CI Dispatch &
    Provider-agnostic module in \file{src/lib/ci/} that sends HTTP
    POST webhooks to GitLab, GitHub, or Bitbucket pipeline trigger
    endpoints with OpenTofu parameters as JSON. \\[4pt]
  Webhook Handler &
    Inbound handler at \route{POST /api/webhooks/\{provider\}/pipeline}.
    Maps CI pipeline status events to order/infrastructure state updates
    and dispatches email notifications on completion or failure. \\[4pt]
  Email &
    Wraps nodemailer. Silently no-ops when SMTP is not configured.
    Configuration is read from environment variables. \\[4pt]
  Bootstrap &
    On startup, seeds the initial Root account from
    \env{ADMIN\_EMAIL} / \env{ADMIN\_PASSWORD} if no users exist. \\[4pt]
  Drizzle ORM &
    Schema definitions and typed query builders in
    \file{src/lib/db/}. All database access goes through Drizzle;
    raw SQL is not used. \\
  \bottomrule
  \caption{Component descriptions}
  \label{tab:components}
\end{longtable}

% ── Level 4 ──────────────────────────────────────────────────
\section{Level 4 — Key Code Flows}
\label{sec:c4-l4}

\subsection{Order Placement Flow (Project Manager)}

\begin{enumerate}
  \item Frontend calls \route{POST /api/catalog/:id/order} with JWT in
        the \code{Authorization} header.
  \item The backend route handler validates the JWT via middleware,
        verifies the request body, and writes an order record with
        status \code{pending\_approval} to PostgreSQL via Drizzle.
  \item The notification module sends an approval-request email to all
        Admins via nodemailer.
  \item An \code{order\_placed} row is appended to the audit log.
  \item The handler returns the new order ID; the frontend navigates
        to the order detail page showing \textit{Awaiting Approval}.
\end{enumerate}

\subsection{Order Approval \& Provisioning Flow}

\begin{enumerate}
  \item Admin calls \route{POST /api/orders/:id/approve}.
  \item The backend handler updates the order status to
        \code{provisioning} and reads the webhook configuration for the
        product-environment pair.
  \item For each configured webhook (ordered by \code{exec\_order}): an
        HTTP POST is sent to the CI provider trigger URL with the
        OpenTofu parameters as JSON.
  \item The CI provider starts a pipeline and returns a pipeline ID.
  \item The backend stores the pipeline ID(s) in the
        \code{pipeline\_ids} JSONB column.
  \item When the CI pipeline completes, the provider calls
        \route{POST /api/webhooks/\{provider\}/pipeline} with the
        result. The webhook handler updates order and infrastructure
        state and sends a deployment-complete email.
  \item On pipeline failure, status becomes \code{failed} and failure
        emails go to the orderer and all Admins.
\end{enumerate}

\subsection{Request–Response Lifecycle (Next.js)}

User interactions are handled by React Server Components or client
components that call the backend REST API via typed wrappers in
\file{src/lib/api.ts}. The backend returns JSON; the frontend
re-renders the affected React subtree. NextAuth v5 maintains the
user session in an encrypted server-side cookie; the session token
is forwarded as a Bearer JWT on every backend API call.

% ─────────────────────────────────────────────────────────────
\chapter{Design Decisions \& Technology Rationale}
\label{ch:design}

\section{Next.js Monorepo}

\textbf{Decision:} The application is structured as a pnpm workspace
monorepo with two Next.js applications (\code{apps/backend} and
\code{apps/frontend}) and a shared types package
(\code{packages/types}).

\textbf{Rationale:}
\begin{itemize}
  \item TypeScript is shared end-to-end: the same interface definitions
        in \file{packages/types/} are consumed by both the backend route
        handlers and the frontend API client, making type drift a
        compile error rather than a runtime surprise.
  \item Separating the backend and frontend into distinct Next.js
        applications allows each to have an independent Dockerfile,
        independent environment variables, and an independent deploy
        cycle. The frontend can be updated without touching the API
        container.
  \item Next.js App Router (both apps) provides file-system-based
        routing, React Server Components, and built-in streaming without
        additional framework glue.
  \item pnpm workspaces deduplicate \code{node\_modules} across
        packages, reducing install size and ensuring consistent package
        versions across the monorepo.
\end{itemize}

\section{React 19 with App Router}

\textbf{Decision:} The frontend is a Next.js 15 application using
React 19 Server and Client Components via the App Router.

\textbf{Rationale:}
\begin{itemize}
  \item \textbf{Type-safe API layer:} All backend calls are made through
        typed wrappers in \file{src/lib/api.ts}. The shared
        \code{packages/types} interfaces guarantee that the shape of
        every response is verified at compile time.
  \item \textbf{Server Components by default:} Data-fetching pages are
        React Server Components that call the backend on the server,
        avoiding client-side waterfall requests and keeping JWTs
        server-side.
  \item \textbf{Incremental interactivity:} Only the components that
        require event handlers or browser APIs are marked
        \code{"use client"}, minimising the client-side JavaScript
        bundle.
\end{itemize}

\section{Tailwind CSS v4}

\textbf{Decision:} Tailwind CSS v4 is used for all styling via the
single \code{@import "tailwindcss"} directive. No DaisyUI. No
separate build step.

\textbf{Rationale:}
\begin{itemize}
  \item \textbf{Zero-config build:} Tailwind v4 uses a native CSS
        engine that requires only the single import; there is no
        \code{tailwind.config.js} or separate \code{build:css} command.
        Next.js handles the PostCSS pass automatically.
  \item \textbf{Design independence:} Pure utility classes keep every
        style decision explicit and auditable. Brand tokens
        (\code{var(--bp)}, \code{var(--bs)}) drive themed surfaces
        without conflicting with a component library's own custom
        properties.
\end{itemize}

\section{PostgreSQL with Drizzle ORM}

\textbf{Decision:} PostgreSQL 15+, accessed via the Drizzle ORM with
the \code{postgres} Node.js driver.

\textbf{Rationale:}
\begin{itemize}
  \item \textbf{Type-safe queries:} Drizzle generates TypeScript types
        from the schema definition in \file{src/lib/db/schema.ts}.
        Every query result is typed; shape mismatches are caught by the
        TypeScript compiler.
  \item \textbf{Schema as code:} \code{drizzle-kit push} applies the
        schema diff directly, removing the need for manually written SQL
        migration files while keeping the schema version-controlled.
  \item \textbf{Thin abstraction:} Drizzle stays close to SQL semantics
        (no opaque magic), making it straightforward to write efficient
        queries for JSONB columns, upserts, and aggregations.
  \item BYTEA columns store product images and the branding logo
        directly in the database, eliminating a separate object store at
        this scale.
\end{itemize}

\section{Two-Container Architecture}

\textbf{Decision:} The backend API and the frontend UI run in separate
containers (\code{apps/backend/Dockerfile} and
\code{apps/frontend/Dockerfile}).

\textbf{Rationale:}
Separating concerns at the container boundary gives each part its own
deployment, scaling, and environment-variable scope. The frontend never
holds database credentials; the backend never renders HTML. Nginx
(or any reverse proxy) routes \code{/api/*} to port 3001 and all other
paths to port 3000. At the anticipated load (tens of users, hundreds
of orders per month), this split adds minimal operational overhead
while making the security boundary explicit.

\section{OpenTofu over Terraform}

\textbf{Decision:} All IaC modules use OpenTofu 1.9+.

\textbf{Rationale:}
OpenTofu is a community-governed, truly open-source fork of Terraform
created after HashiCorp changed Terraform's license to BSL 1.1 in 2023.
The API, HCL syntax, provider ecosystem, and state format are fully
compatible. Using OpenTofu avoids future licensing costs and complies
with Open Hybrid Cloud's open-source software policy.

\section{GitLab Managed Terraform State}

\textbf{Decision:} OpenTofu state is stored in GitLab's built-in
HTTP-compatible state backend (GitLab Managed Terraform State).

\textbf{Rationale:}
\begin{itemize}
  \item Reuses existing GitLab infrastructure — no S3 bucket, no
        Terraform Cloud account, no Vault setup required.
  \item State is protected by GitLab's RBAC: only project members with
        Developer or higher access can read or modify state.
  \item State locking via HTTP \code{LOCK}/\code{UNLOCK} prevents
        concurrent apply operations.
  \item State is browsable in the GitLab UI under
        \textbf{Infrastructure → Terraform states}.
\end{itemize}

\section{Per-Resource Isolated State}

\textbf{Decision:} Each VM and each Kubernetes cluster has its own
isolated OpenTofu state (named \code{vm-\{label\}} and
\code{k8s-\{label\}}).

\textbf{Rationale:}
Shared state across multiple VMs creates blast-radius risk: a failing
\code{apply} for one VM could lock the state and block unrelated VMs.
Isolated states mean each resource's lifecycle is entirely independent.
The trade-off is a larger number of state files, which is manageable
at the expected scale.

\section{Webhook-Driven Pipeline Trigger}

\textbf{Decision:} The webshop triggers GitLab pipelines via webhook
(HTTP POST) rather than the GitLab API's pipeline-trigger endpoint.

\textbf{Rationale:}
Webhooks are the native GitLab mechanism for external triggers. They
carry a secure token for authentication and include the ability to pass
variables (OpenTofu parameters) as JSON. The pipeline configuration
(\file{.gitlab-ci.yml}) lives in the same repository as the IaC code,
making the trigger configuration auditable and version-controlled.

\section{Internationalization: 25 Languages}

\textbf{Decision:} All UI strings are externalized in a key-value i18n
map covering 25 languages (all EU official languages plus Russian and
Ukrainian).

\textbf{Rationale:}
Open Hybrid Cloud operates across Europe. The map is defined in
\file{internal/i18n/i18n.go} as a Go map literal for compile-time
completeness checking. Translation of product content (not UI strings)
is delegated to the optional AI translation service.

\section{Session Security: Encrypted Cookies}

\textbf{Decision:} User sessions are stored in encrypted, signed HTTP
cookies — not in the database or server-side session store.

\textbf{Rationale:}
\begin{itemize}
  \item No database round-trip on every request to look up a session.
  \item Horizontal scaling is trivial: no shared session store required.
  \item The \code{SESSION\_KEY} (32-byte, hex-encoded) is used to both
        sign and encrypt the cookie content via AES-GCM, so the server
        can verify integrity without a separate HMAC key.
  \item Cookies are set with \code{HttpOnly}, \code{Secure}, and
        \code{SameSite=Lax} to mitigate XSS session theft and CSRF.
  \item Logout invalidates the session by overwriting the cookie with an
        empty, expired value — no server-side revocation list needed for
        the MVP threat model.
\end{itemize}

\textbf{Alternative considered:} Server-side sessions in PostgreSQL.
Rejected to avoid the extra table and join on every authenticated
request. If revocation of individual sessions at scale is required this
can be introduced as a future enhancement.

\section{Password Hashing: bcrypt}

\textbf{Decision:} Local user passwords are hashed with bcrypt (cost
factor~12) via \code{golang.org/x/crypto/bcrypt}.

\textbf{Rationale:}
\begin{itemize}
  \item bcrypt is an adaptive, memory-hard function specifically designed
        for password storage; it is resistant to GPU-accelerated
        dictionary attacks.
  \item Cost factor~12 takes ~250\,ms on modern hardware — slow enough
        to deter brute-force while still acceptable for interactive login.
  \item The Go standard-library-adjacent \code{x/crypto} package is
        actively maintained by the Go team.
  \item Passwords are never stored in plaintext or with reversible
        encryption.
\end{itemize}

\textbf{Alternative considered:} Argon2id. More modern, but bcrypt is
widely understood, well-tested in Go, and sufficient for the low
login-volume use case.

\section{Static Asset Embedding: \texttt{embed.FS}}

\textbf{Decision:} HTML templates and static assets (CSS, JS, images)
are embedded into the Go binary at compile time using the
\code{//go:embed} directive and \code{embed.FS}.

\textbf{Rationale:}
\begin{itemize}
  \item The resulting binary is fully self-contained — no external
        file system paths need to match the deployment environment.
  \item Deployment is a single \code{COPY} in the Dockerfile (multi-stage
        build); no volume mounts are required for templates.
  \item Template changes are compiled into the binary, so a deployment
        is always atomic: the binary and its templates are in sync.
  \item The Go compiler resolves embed paths at build time, making
        missing-file bugs a compile error rather than a runtime panic.
\end{itemize}

\textbf{Trade-off:} Hot-reloading templates during development is not
possible without restarting the server. The \code{make dev} target runs
the server with \code{go run}, so a simple restart is fast enough for
the development workflow.

% ─────────────────────────────────────────────────────────────
%  PART II — INFRASTRUCTURE AS CODE
% ─────────────────────────────────────────────────────────────
\part{Infrastructure as Code}
\label{part:iac}

% ─────────────────────────────────────────────────────────────
\chapter{GitLab Repository Concept}
\label{ch:gitlab-concept}

\section{Overview}

The IaC layer consists of six GitLab repositories in the \code{open-hybrid-cloud}
group. Each repository is a self-contained OpenTofu module with its own
CI/CD pipeline and state. Together they provision all cloud
infrastructure on Linode/Akamai.

\begin{table}[H]
  \centering
  \caption{GitLab repository overview}
  \label{tab:repos}
  \begin{tabularx}{\linewidth}{@{}l>{\raggedright\arraybackslash}Xl@{}}
    \toprule
    \textbf{Repository} & \textbf{Purpose} & \textbf{Trigger} \\
    \midrule
    \code{network-core}   & VPC, subnets, base firewall, DNS zone & Manual \\
    \code{vm-platform}    & Linode VM instances (per-VM) & Webhook \\
    \code{k8s-platform}   & LKE Kubernetes clusters (per-cluster) & Webhook \\
    \code{shared-services}& GitLab CE + Vault + Registry & Manual \\
    \code{observability}  & Grafana + Prometheus + Loki & Manual \\
    \code{infra-state}    & State backend host (no IaC code) & N/A \\
    \bottomrule
  \end{tabularx}
\end{table}

\section{Repository File Structure}

Every module repository (except \code{infra-state}) follows the same
file layout:

\begin{lstlisting}[style=bash]
<module>/
+-- .gitlab-ci.yml   # CI/CD pipeline definition
+-- backend.tf       # HTTP state backend (GitLab Managed)
+-- provider.tf      # Linode provider + required versions
+-- variables.tf     # Input variable declarations
+-- main.tf          # Resource definitions
+-- outputs.tf       # Output values
\end{lstlisting}

\section{State Management}

All state files live in the \code{infra-state} project. The project
hosts no IaC code; it is solely a container for GitLab Managed Terraform
State files.

\textbf{State naming convention:}

\begin{table}[H]
  \centering
  \caption{State name convention per module}
  \begin{tabular}{@{}ll@{}}
    \toprule
    \textbf{Module} & \textbf{State name} \\
    \midrule
    \code{network-core}    & \code{network-core} \\
    \code{vm-platform}     & \code{vm-\{vm\_label\}} \\
    \code{k8s-platform}    & \code{k8s-\{cluster\_label\}} \\
    \code{shared-services} & \code{shared-prod} \\
    \code{observability}   & \code{observability-prod} \\
    \bottomrule
  \end{tabular}
\end{table}

The backend URL pattern is:
\begin{lstlisting}[style=bash]
https://<gitlab-host>/api/v4/projects/<INFRA_STATE_PROJECT_ID>/terraform/state/<STATE_NAME>
\end{lstlisting}

Backend configuration is passed at \code{tofu init} time via
\code{-backend-config} flags, not hard-coded in \file{backend.tf}.
This keeps credentials out of version control.

\section{CI/CD Pipeline Stages}

All module pipelines share the same three-stage structure:

\begin{enumerate}
  \item \textbf{validate} — \code{tofu validate}: checks HCL syntax and
        provider schema compliance.
  \item \textbf{plan} — \code{tofu plan -out=tfplan}: computes the
        diff and saves the plan artifact.
  \item \textbf{apply} — \code{tofu apply tfplan}: applies the plan.
        For webhook-triggered modules, apply runs automatically on
        pipeline success. For singleton modules (\code{shared-services},
        \code{observability}, \code{network-core}), the apply job is
        \code{when: manual} to require deliberate human confirmation.
\end{enumerate}

\textbf{Destroy flow:} Webhook-triggered modules (\code{vm-platform},
\code{k8s-platform}) accept a \code{TF\_ACTION=destroy} variable. When
set, the apply stage runs \code{tofu destroy -auto-approve} instead of
\code{tofu apply}.

Listing~\ref{lst:gitlab-ci-vm} shows the canonical \file{.gitlab-ci.yml}
for the \code{vm-platform} module. Singleton modules differ only in the
\code{apply} job: \code{when: manual} replaces \code{when: on\_success},
and there is no destroy branch.

\begin{lstlisting}[style=yaml,caption={.gitlab-ci.yml for vm-platform (webhook-triggered module)},label={lst:gitlab-ci-vm}]
image: ghcr.io/opentofu/opentofu:1.9

variables:
  TF_ACTION: "apply"
  TF_STATE_NAME: "vm-${vm_label}"
  TF_VAR_linode_token: "${LINODE_TOKEN}"

.tofu_init: &tofu_init
  before_script:
    - tofu init
        -reconfigure
        -backend-config="address=${CI_API_V4_URL}/projects/${INFRA_STATE_PROJECT_ID}/terraform/state/${TF_STATE_NAME}"
        -backend-config="lock_address=${CI_API_V4_URL}/projects/${INFRA_STATE_PROJECT_ID}/terraform/state/${TF_STATE_NAME}/lock"
        -backend-config="unlock_address=${CI_API_V4_URL}/projects/${INFRA_STATE_PROJECT_ID}/terraform/state/${TF_STATE_NAME}/lock"
        -backend-config="username=gitlab-ci-token"
        -backend-config="password=${CI_JOB_TOKEN}"
        -backend-config="lock_method=POST"
        -backend-config="unlock_method=DELETE"
        -backend-config="retry_wait_min=5"

stages:
  - validate
  - plan
  - apply

validate:
  stage: validate
  <<: *tofu_init
  script:
    - tofu validate
  rules:
    - if: $CI_PIPELINE_SOURCE == "trigger"

plan:
  stage: plan
  <<: *tofu_init
  script:
    - tofu plan -out=tfplan
  artifacts:
    paths:
      - tfplan
    expire_in: 1 hour
  rules:
    - if: $CI_PIPELINE_SOURCE == "trigger"

apply:
  stage: apply
  <<: *tofu_init
  script:
    - |
      if [ "${TF_ACTION}" = "destroy" ]; then
        tofu destroy -auto-approve
      else
        tofu apply -auto-approve tfplan
      fi
  dependencies:
    - plan
  rules:
    - if: $CI_PIPELINE_SOURCE == "trigger" && $TF_ACTION == "destroy"
      when: always
    - if: $CI_PIPELINE_SOURCE == "trigger"
      when: on_success
\end{lstlisting}

Listing~\ref{lst:gitlab-ci-singleton} shows a complete pipeline for
singleton modules (\code{network-core}, \code{shared-services},
\code{observability}) where a human must confirm the apply step:

\begin{lstlisting}[style=yaml,caption={.gitlab-ci.yml for singleton modules (manual apply)},label={lst:gitlab-ci-singleton}]
image: ghcr.io/opentofu/opentofu:1.9

variables:
  TF_STATE_NAME: "shared-prod"
  TF_VAR_linode_token: "${LINODE_TOKEN}"

.tofu_init: &tofu_init
  before_script:
    - tofu init
        -backend-config="address=${CI_API_V4_URL}/projects/${INFRA_STATE_PROJECT_ID}/terraform/state/${TF_STATE_NAME}"
        -backend-config="lock_address=${CI_API_V4_URL}/projects/${INFRA_STATE_PROJECT_ID}/terraform/state/${TF_STATE_NAME}/lock"
        -backend-config="unlock_address=${CI_API_V4_URL}/projects/${INFRA_STATE_PROJECT_ID}/terraform/state/${TF_STATE_NAME}/lock"
        -backend-config="username=gitlab-ci-token"
        -backend-config="password=${CI_JOB_TOKEN}"
        -backend-config="lock_method=POST"
        -backend-config="unlock_method=DELETE"
        -backend-config="retry_wait_min=5"

stages:
  - validate
  - plan
  - apply

validate:
  stage: validate
  <<: *tofu_init
  script:
    - tofu validate
  rules:
    - if: $CI_COMMIT_BRANCH == "main"

plan:
  stage: plan
  <<: *tofu_init
  script:
    - tofu plan -out=tfplan
  artifacts:
    paths:
      - tfplan
    expire_in: 1 hour
  rules:
    - if: $CI_COMMIT_BRANCH == "main"

apply:
  stage: apply
  <<: *tofu_init
  script:
    - tofu apply -auto-approve tfplan
  dependencies:
    - plan
  rules:
    - if: $CI_COMMIT_BRANCH == "main"
      when: manual
\end{lstlisting}

\notebox{The single required CI/CD variable to set in the \textit{infra-state}
GitLab project group is \code{INFRA\_STATE\_PROJECT\_ID} — the numeric project
ID of the \code{infra-state} repository (visible in GitLab under
\textbf{Settings → General}). \code{CI\_JOB\_TOKEN} and \code{CI\_API\_V4\_URL}
are provided automatically by GitLab CI. \code{LINODE\_TOKEN} must be
set with Read/Write API access.}

\section{Webhook Integration with the Webshop}
\label{sec:webhook}

\begin{enumerate}
  \item An Admin approves an order in the webshop (or places one
        directly).
  \item For each webhook configured on the product-environment
        combination, the webshop sends:
\begin{lstlisting}[style=bash]
POST <gitlab-webhook-url>
X-Gitlab-Token: <secret>
Content-Type: application/json

{
  "ref": "main",
  "variables": [
    {"key": "TF_VAR_vm_label",  "value": "myvm-01"},
    {"key": "TF_VAR_vpc_id",    "value": "12345"},
    ...
  ]
}
\end{lstlisting}
  \item GitLab starts a pipeline for the \code{main} branch, injecting
        the variables as environment variables.
  \item The pipeline reads \code{TF\_VAR\_*} variables, runs
        \code{tofu plan} then \code{tofu apply}.
  \item On completion (success or failure), the webshop's polling
        goroutine detects the status change and updates the order record.
\end{enumerate}

\section{Dependency Between Modules}

\begin{figure}[H]
\centering
\begin{tikzpicture}[node distance=1.0cm and 2.0cm,
  dep/.style={rectangle, draw=ohc-blue!60, fill=ohc-blue!10,
              text width=3cm, align=center, minimum height=1.2cm,
              font=\small\bfseries},
  dep-ext/.style={rectangle, draw=gray!60, fill=gray!10,
                  text width=3cm, align=center, minimum height=1.2cm,
                  font=\small},
  arr/.style={->, >=Stealth, thick, gray!70}]

  \node[dep] (nc)  {network-core};
  \node[dep, right=2.5cm of nc] (vm)  {vm-platform};
  \node[dep, right=of vm]        (k8s) {k8s-platform};
  \node[dep, below=1.2cm of nc]  (ss)  {shared-services};
  \node[dep, right=of ss]        (obs) {observability};
  \node[dep-ext, below right=1.2cm and 0.5cm of nc, text width=2.2cm]
        (is) {infra-state\\\scriptsize(state host)};

  \draw[arr] (nc) -- node[c4label,above]{\scriptsize vpc\_id, subnet\_id, firewall\_id} (vm);
  \draw[arr] (nc) -- node[c4label,above]{\scriptsize vpc\_id, subnet\_id} (k8s);
  \draw[arr] (nc) -- (ss);
  \draw[arr] (nc) -- (obs);

\end{tikzpicture}
\caption{Module dependency graph}
\label{fig:module-deps}
\end{figure}

\code{network-core} must be applied first. Its outputs (\code{vpc\_id},
\code{subnet\_ids}, \code{firewall\_id}) are passed as input variables
to all other modules.

% ─────────────────────────────────────────────────────────────
\chapter{OpenTofu Modules}
\label{ch:modules}

\section{network-core}

\textbf{Purpose:} Foundational network infrastructure. Apply once per
environment; no webhook trigger.

\begin{description}
  \item[Resources created:]
    \code{linode\_vpc} (VPC), \code{linode\_vpc\_subnet} (subnets via
    \code{for\_each}), \code{linode\_firewall} (base inbound/outbound
    policy), \code{linode\_domain} (optional DNS zone).
  \item[Key design choice:]
    Subnets are defined as a \code{map(object(\{cidr, description\}))}
    variable. This allows adding subnets by editing a single variable
    without changing the resource code.
  \item[Key outputs:]
    \code{vpc\_id}, \code{subnet\_ids} (map: label → ID),
    \code{firewall\_id}, \code{dns\_zone\_id}.
\end{description}

\section{vm-platform}

\textbf{Purpose:} Provision individual Linode VMs on demand. One state
per VM (\code{vm-\{label\}}). Webhook-triggered by the webshop.

\begin{description}
  \item[Resources created:]
    \code{linode\_firewall} (VM-specific), \code{linode\_instance},
    \code{linode\_firewall\_device} (attaches firewall to VM),
    \code{linode\_volume} (optional block storage),
    \code{linode\_domain\_record} (optional A record).
  \item[Key design choice:]
    The VM gets its own firewall (in addition to the base firewall from
    \code{network-core}) to allow per-VM port rules without affecting
    the shared base policy.
  \item[Destroy flow:]
    Triggered by the webshop decommission action.
    \code{TF\_ACTION=destroy} → \code{tofu destroy -auto-approve}.
\end{description}

\section{k8s-platform}

\textbf{Purpose:} Provision Linode Kubernetes Engine (LKE) clusters.
One state per cluster (\code{k8s-\{label\}}). Webhook-triggered.

\begin{description}
  \item[Resources created:]
    \code{linode\_firewall} (cluster-specific), \code{linode\_lke\_cluster}
    with dynamic \code{pool} blocks (supports multiple node pools with
    optional autoscaler), \code{linode\_domain\_record} (optional).
  \item[Key output:]
    \code{kubeconfig} (base64-encoded, marked \code{sensitive}) —
    retrieve with \code{tofu output -raw kubeconfig | base64 -d}.
  \item[Node pool design:]
    Node pools are a \code{list(object)} variable with an optional
    \code{autoscaler} sub-object, allowing any combination of fixed-size
    and auto-scaling pools in a single cluster.
\end{description}

\section{shared-services}

\textbf{Purpose:} Long-lived shared services: GitLab CE, HashiCorp
Vault, container registry. Single state (\code{shared-prod}).
Manual apply.

\begin{description}
  \item[Resources created:]
    Two \code{linode\_instance} resources (GitLab, Vault), two
    \code{linode\_volume} resources (data volumes), one
    \code{linode\_firewall} with tailored inbound rules (HTTP/HTTPS/Git
    SSH for GitLab; Vault API 8200 restricted to RFC1918), two
    \code{linode\_firewall\_device} attachments, optional DNS A records.
  \item[Operational note:]
    GitLab CE and Vault are installed via post-provisioning scripts
    (cloud-init or Ansible), not managed by OpenTofu. OpenTofu only
    provisions the infrastructure layer.
\end{description}

\section{observability}

\textbf{Purpose:} Grafana, Prometheus, and Loki on a single VM.
Single state (\code{observability-prod}). Manual apply.

\begin{description}
  \item[Resources created:]
    \code{linode\_instance}, \code{linode\_volume} (200 GB default for
    metrics and logs), \code{linode\_firewall} (Grafana port
    configurable, Prometheus/Loki restricted to RFC1918), optional DNS
    A record.
  \item[Key output:]
    \code{grafana\_url} — \code{http://\{ip\}:\{port\}}.
\end{description}

% ─────────────────────────────────────────────────────────────
%  PART III — ADMINISTRATOR GUIDE
% ─────────────────────────────────────────────────────────────
\part{Administrator Guide}
\label{part:admin}

% ─────────────────────────────────────────────────────────────
\chapter{Initial Setup \& Installation}
\label{ch:setup}

\section{Prerequisites}

\begin{itemize}
  \item Docker 24+ (or a Kubernetes cluster)
  \item PostgreSQL 15+ (external or containerized)
  \item SMTP server credentials (optional, can be configured later)
  \item Microsoft Entra ID application registration for OIDC
        (optional for local-only operation)
  \item Linode API token with Read/Write scope
  \item GitLab instance with webhook support
\end{itemize}

\section{Environment Variables}

The webshop is configured entirely via environment variables. Copy
\file{.env.example} to \file{.env} and populate the following:

\begin{table}[H]
  \centering
  \caption{Required environment variables}
  \begin{tabularx}{\linewidth}{@{}l>{\raggedright\arraybackslash}Xl@{}}
    \toprule
    \textbf{Variable} & \textbf{Description} & \textbf{Required} \\
    \midrule
    \env{DATABASE\_URL}     & PostgreSQL DSN                         & Yes \\
    \env{SESSION\_KEY}      & 32-byte hex session encryption key      & Yes \\
    \env{ADMIN\_EMAIL}      & Initial Root email             & Yes \\
    \env{ADMIN\_PASSWORD}   & Initial Root password          & Yes \\
    \env{BASE\_URL}         & Public URL of the webshop               & Yes \\
    \env{OIDC\_CLIENT\_ID}     & Entra ID application client ID      & No  \\
    \env{OIDC\_CLIENT\_SECRET} & Entra ID client secret              & No  \\
    \env{OIDC\_ISSUER}         & Entra ID issuer URL                 & No  \\
    \env{SMTP\_HOST}        & SMTP host (overridable in Admin UI)     & No  \\
    \env{SMTP\_PORT}        & SMTP port (default 587)                 & No  \\
    \env{SMTP\_FROM}        & Sender address                          & No  \\
    \env{SMTP\_USERNAME}    & SMTP username                           & No  \\
    \env{SMTP\_PASSWORD}    & SMTP password                           & No  \\
    \env{AI\_PROVIDER}      & AI translation provider (startup only)  & No  \\
    \bottomrule
  \end{tabularx}
\end{table}

\notebox{SMTP and AI translation can also be configured (and overridden)
through the Admin UI at \route{/admin/smtp} and \route{/admin/ai-config}.
Database settings take precedence over environment variables at runtime.}

\section{Deployment on a Docker Host}
\label{sec:docker-deploy}

This section describes a production-grade deployment on a single Linux
host using Docker and an Nginx reverse proxy with TLS termination.

\subsection*{Architecture}

\begin{figure}[H]
\centering
\resizebox{\textwidth}{!}{%
\begin{tikzpicture}[node distance=1.2cm and 1.6cm,
  box/.style={rectangle, draw=ohc-blue!70, fill=ohc-blue!10,
              text width=2.8cm, align=center, minimum height=1.1cm, font=\small\bfseries},
  db/.style={cylinder, draw=c4-database!80, fill=c4-database!20,
             shape border rotate=90, text width=2.2cm, align=center,
             minimum height=1.2cm, font=\small\bfseries},
  ext/.style={rectangle, draw=gray!60, fill=gray!10, dashed,
              text width=2.4cm, align=center, minimum height=1.0cm, font=\small},
  arr/.style={->, >=Stealth, thick, gray!60}]

  \node[ext] (client) {Browser\\/ API Client};
  \node[box, right=1.6cm of client] (nginx) {Nginx\\\scriptsize TLS termination\\reverse proxy};
  \node[box, right=1.6cm of nginx] (app) {open-hybrid-cloud\\\scriptsize Docker\\:8080};
  \node[db, right=1.6cm of app] (pg) {PostgreSQL\\\scriptsize :5432};
  \node[ext, below=1.2cm of nginx] (letsenc) {Let's Encrypt\\\scriptsize or Corporate CA};

  \draw[arr] (client) -- node[above,font=\tiny]{HTTPS:443} (nginx);
  \draw[arr] (nginx)  -- node[above,font=\tiny]{HTTP:8080} (app);
  \draw[arr] (app)    -- node[above,font=\tiny]{TCP:5432} (pg);
  \draw[arr, dashed] (letsenc) -- node[right,font=\tiny]{cert} (nginx);

\end{tikzpicture}}%
\caption{Docker Host deployment architecture}
\label{fig:docker-arch}
\end{figure}

\subsection*{Step-by-Step Deployment Procedure}

\begin{enumerate}

\item \textbf{Install Docker and Docker Compose.}
\begin{lstlisting}[style=bash]
# Debian/Ubuntu
apt-get install -y docker.io docker-compose-v2
systemctl enable --now docker
\end{lstlisting}

\item \textbf{Clone the repository and build the image.}
\begin{lstlisting}[style=bash]
git clone https://github.com/Maximilian-Maag/open-hybrid-cloud.git
cd open-hybrid-cloud
make docker-build
# or pull from Docker Hub:
docker pull maximilianmaag/open-hybrid-cloud:latest
\end{lstlisting}

\item \textbf{Create the environment file.}
\begin{lstlisting}[style=bash]
cp infra/docker-host/.env.example infra/docker-host/.env
# Edit .env with a text editor; set at minimum:
#   DATABASE_URL, SESSION_KEY, ADMIN_EMAIL, ADMIN_PASSWORD, BASE_URL
\end{lstlisting}

\item \textbf{Start PostgreSQL and the application.}
\begin{lstlisting}[style=bash]
cd infra/docker-host
docker compose up -d
\end{lstlisting}

\item \textbf{Run database migrations.}
\begin{lstlisting}[style=bash]
docker exec open-hybrid-cloud /migrate
\end{lstlisting}

\item \textbf{Obtain a TLS certificate.}

\textit{Option A — Let's Encrypt (public domain):}
\begin{lstlisting}[style=bash]
apt-get install -y certbot python3-certbot-nginx
certbot --nginx -d shop.example.com
\end{lstlisting}

\textit{Option B — Corporate CA (internal PKI):} Place the signed
certificate and key at the paths referenced in
\file{infra/docker-host/nginx.conf} (see below) and restart Nginx.

\item \textbf{Configure Nginx as TLS-terminating reverse proxy.}

Listing~\ref{lst:nginxconf} shows a minimal but production-ready
Nginx configuration:

\begin{lstlisting}[style=yaml,caption={infra/docker-host/nginx.conf},label={lst:nginxconf}]
server {
    listen 80;
    server_name shop.example.com;
    return 301 https://$host$request_uri;
}

server {
    listen 443 ssl http2;
    server_name shop.example.com;

    ssl_certificate     /etc/letsencrypt/live/shop.example.com/fullchain.pem;
    ssl_certificate_key /etc/letsencrypt/live/shop.example.com/privkey.pem;
    ssl_protocols       TLSv1.2 TLSv1.3;
    ssl_ciphers         HIGH:!aNULL:!MD5;

    client_max_body_size 10m;

    location / {
        proxy_pass         http://127.0.0.1:8080;
        proxy_set_header   Host              $host;
        proxy_set_header   X-Real-IP         $remote_addr;
        proxy_set_header   X-Forwarded-For   $proxy_add_x_forwarded_for;
        proxy_set_header   X-Forwarded-Proto $scheme;
        proxy_read_timeout 60s;
    }
}
\end{lstlisting}

\item \textbf{Reload Nginx.}
\begin{lstlisting}[style=bash]
nginx -t && systemctl reload nginx
\end{lstlisting}

\item \textbf{Verify the deployment.}

Navigate to \url{https://shop.example.com} and log in with
\env{ADMIN\_EMAIL} / \env{ADMIN\_PASSWORD}. Change the password
immediately under \textbf{Settings → My Profile}.

\item \textbf{(Optional) Enable automatic certificate renewal.}
\begin{lstlisting}[style=bash]
# Certbot installs a systemd timer automatically
systemctl status certbot.timer
\end{lstlisting}

\end{enumerate}

\subsection*{Backup \& Restore}

\begin{lstlisting}[style=bash]
# Backup PostgreSQL
docker exec webshop-postgres pg_dump -U webshop webshop \
  | gzip > backup-$(date +%Y%m%d).sql.gz

# Restore
zcat backup-20260101.sql.gz \
  | docker exec -i webshop-postgres psql -U webshop webshop
\end{lstlisting}

\section{Deployment on Kubernetes}
\label{sec:k8s-deploy}

This section covers deploying the webshop to an existing Kubernetes
cluster (e.g.\ the LKE cluster provisioned by \code{k8s-platform}).

\subsection*{Architecture}

\begin{figure}[H]
\centering
\resizebox{\textwidth}{!}{%
\begin{tikzpicture}[node distance=1.2cm and 1.8cm,
  pod/.style={rectangle, draw=c4-container!80, fill=c4-container!15,
              text width=2.8cm, align=center, minimum height=1.0cm, font=\small\bfseries},
  svc/.style={rectangle, rounded corners=4pt, draw=ohc-amber!80, fill=ohc-amber!20,
              text width=2.4cm, align=center, minimum height=0.9cm, font=\scriptsize\bfseries},
  ext/.style={rectangle, draw=gray!60, fill=gray!10, dashed,
              text width=2.4cm, align=center, minimum height=0.9cm, font=\small},
  arr/.style={->, >=Stealth, thick, gray!60}]

  \node[ext] (client) {Browser};
  \node[svc, right=1.8cm of client] (ing) {Ingress\\(Nginx)};
  \node[pod, right=1.8cm of ing] (app) {open-hybrid-cloud\\Pod(s)};
  \node[ext, right=1.8cm of app] (pg) {PostgreSQL\\\scriptsize external};
  \node[svc, below=1.0cm of ing] (cm) {cert-manager\\ClusterIssuer};
  \node[svc, below=1.0cm of app] (hpa) {HPA};

  \draw[arr] (client) -- node[above,font=\tiny]{HTTPS} (ing);
  \draw[arr] (ing) -- node[above,font=\tiny]{:8080} (app);
  \draw[arr] (app) -- node[above,font=\tiny]{:5432} (pg);
  \draw[arr, dashed] (cm) -- (ing);
  \draw[arr, dashed] (hpa) -- (app);

\end{tikzpicture}}%
\caption{Kubernetes deployment architecture}
\label{fig:k8s-arch}
\end{figure}

\subsection*{Prerequisites}

\begin{itemize}
  \item \code{kubectl} and \code{helm} (v3.12+) configured for the target cluster
  \item Nginx Ingress Controller installed (\code{ingress-nginx})
  \item cert-manager installed with a \code{ClusterIssuer} for Let's
        Encrypt or a corporate CA
  \item The image \code{maximilianmaag/open-hybrid-cloud:\textit{tag}} is publicly
        available on Docker Hub — no \code{imagePullSecret} required
\end{itemize}

\subsection*{Deployment with Helm}

The repository ships a Helm chart at \file{infra/helm/open-hybrid-cloud/}.
It covers the full deployment in a single command and handles database
migrations automatically as a pre-install/pre-upgrade hook.

\begin{lstlisting}[style=bash,caption={Helm install with required values},label={lst:helm-install}]
helm upgrade --install open-hybrid-cloud \
  infra/helm/open-hybrid-cloud \
  --namespace open-hybrid-cloud \
  --create-namespace \
  --set env.databaseUrl="postgres://user:pass@pg.example.com:5432/webshop?sslmode=require" \
  --set env.sessionSecret="<32-byte-hex>" \
  --set env.adminPassword="<initial-password>" \
  --set ingress.hosts[0].host=shop.example.com \
  --set ingress.tls[0].hosts[0]=shop.example.com \
  --set ingress.tls[0].secretName=open-hybrid-cloud-tls
\end{lstlisting}

\notebox{Sensitive values should be passed via a separate
\file{secrets.values.yaml} file (not committed to version control)
rather than as \code{--set} arguments, so they do not appear in shell
history.}

\begin{lstlisting}[style=bash,caption={Example secrets.values.yaml (do not commit)},label={lst:helm-secrets}]
env:
  databaseUrl: "postgres://user:pass@pg.example.com:5432/webshop?sslmode=require"
  sessionSecret: "aabbccddeeff00112233445566778899aabbccddeeff00112233445566778899"
  adminPassword: "change-me-immediately"
  entra:
    tenantId: "xxxxxxxx-xxxx-xxxx-xxxx-xxxxxxxxxxxx"
    clientId: "xxxxxxxx-xxxx-xxxx-xxxx-xxxxxxxxxxxx"
    clientSecret: "your-client-secret"
    redirectUrl: "https://shop.example.com/auth/callback"
\end{lstlisting}

\begin{lstlisting}[style=bash]
helm upgrade --install open-hybrid-cloud infra/helm/open-hybrid-cloud \
  --namespace open-hybrid-cloud --create-namespace \
  -f values.production.yaml \
  -f secrets.values.yaml
\end{lstlisting}

Table~\ref{tab:helm-values} lists the most important configurable values.

\begin{table}[H]
  \centering
  \caption{Key Helm values}
  \label{tab:helm-values}
  \begin{tabularx}{\linewidth}{@{}l>{\raggedright\arraybackslash}Xl@{}}
    \toprule
    \textbf{Key} & \textbf{Description} & \textbf{Default} \\
    \midrule
    \code{image.repository}          & Docker Hub image name          & \code{maximilianmaag/open-hybrid-cloud} \\
    \code{image.tag}                  & Image tag (empty = appVersion) & \code{""} \\
    \code{replicaCount}               & Deployment replicas            & \code{2} \\
    \code{env.databaseUrl}            & PostgreSQL DSN (required)      & — \\
    \code{env.sessionSecret}          & Session encryption key (req.)  & — \\
    \code{env.adminPassword}          & Initial admin password (req.)  & — \\
    \code{ingress.hosts}              & Ingress host list              & \code{shop.example.com} \\
    \code{ingress.tls}                & TLS configuration              & (see values.yaml) \\
    \code{autoscaling.enabled}        & Enable HPA                     & \code{false} \\
    \code{autoscaling.maxReplicas}    & HPA max replica count          & \code{6} \\
    \code{migrate.enabled}            & Run DB migrations as hook      & \code{true} \\
    \bottomrule
  \end{tabularx}
\end{table}

\subsection*{Step-by-Step Manual Deployment (without Helm)}

\begin{enumerate}

\item \textbf{Create the namespace.}
\begin{lstlisting}[style=bash]
kubectl create namespace open-hybrid-cloud
\end{lstlisting}

\item \textbf{(Optional) Create an image pull secret.}

The container image \code{maximilianmaag/open-hybrid-cloud} is publicly
available on Docker Hub and requires no authentication. Skip this step
for standard deployments. Only required if you mirror the image to a
private registry:
\begin{lstlisting}[style=bash]
kubectl create secret docker-registry my-registry-secret \
  --namespace open-hybrid-cloud \
  --docker-server=<your-registry> \
  --docker-username=<username> \
  --docker-password=<password>
\end{lstlisting}

\item \textbf{Create the application Secret.}
\begin{lstlisting}[style=yaml,caption={Kubernetes Secret for the webshop},label={lst:k8s-secret}]
apiVersion: v1
kind: Secret
metadata:
  name: open-hybrid-cloud-env
  namespace: open-hybrid-cloud
type: Opaque
stringData:
  DATABASE_URL: "postgres://webshop:password@pg.example.com:5432/webshop?sslmode=require"
  SESSION_KEY: "000102030405060708090a0b0c0d0e0f101112131415161718191a1b1c1d1e1f"
  ADMIN_EMAIL: "admin@example.com"
  ADMIN_PASSWORD: "changeme"
  BASE_URL: "https://shop.example.com"
\end{lstlisting}

\item \textbf{Run database migrations as a Kubernetes Job.}
\begin{lstlisting}[style=yaml,caption={Migration Job},label={lst:k8s-migrate}]
apiVersion: batch/v1
kind: Job
metadata:
  name: open-hybrid-cloud-migrate
  namespace: open-hybrid-cloud
spec:
  template:
    spec:
      restartPolicy: Never
      containers:
        - name: migrate
          image: maximilianmaag/open-hybrid-cloud:latest
          command: ["/migrate"]
          envFrom:
            - secretRef:
                name: open-hybrid-cloud-env
\end{lstlisting}

\begin{lstlisting}[style=bash]
kubectl apply -f migrate-job.yaml
kubectl wait --for=condition=complete job/open-hybrid-cloud-migrate \
  -n open-hybrid-cloud --timeout=120s
\end{lstlisting}

\item \textbf{Deploy the application.}
\begin{lstlisting}[style=yaml,caption={Deployment and Service},label={lst:k8s-deployment}]
apiVersion: apps/v1
kind: Deployment
metadata:
  name: open-hybrid-cloud
  namespace: open-hybrid-cloud
spec:
  replicas: 2
  selector:
    matchLabels:
      app: open-hybrid-cloud
  template:
    metadata:
      labels:
        app: open-hybrid-cloud
    spec:
      containers:
        - name: app
          image: maximilianmaag/open-hybrid-cloud:latest
          ports:
            - containerPort: 8080
          envFrom:
            - secretRef:
                name: open-hybrid-cloud-env
          livenessProbe:
            httpGet:
              path: /health
              port: 8080
            initialDelaySeconds: 10
            periodSeconds: 30
          readinessProbe:
            httpGet:
              path: /health
              port: 8080
            initialDelaySeconds: 5
            periodSeconds: 10
          resources:
            requests:
              cpu: "100m"
              memory: "128Mi"
            limits:
              cpu: "500m"
              memory: "512Mi"
---
apiVersion: v1
kind: Service
metadata:
  name: open-hybrid-cloud
  namespace: open-hybrid-cloud
spec:
  selector:
    app: open-hybrid-cloud
  ports:
    - port: 80
      targetPort: 8080
\end{lstlisting}

\item \textbf{Configure the Ingress with TLS.}
\begin{lstlisting}[style=yaml,caption={Ingress with cert-manager TLS},label={lst:k8s-ingress}]
apiVersion: networking.k8s.io/v1
kind: Ingress
metadata:
  name: open-hybrid-cloud
  namespace: open-hybrid-cloud
  annotations:
    nginx.ingress.kubernetes.io/proxy-body-size: "10m"
    cert-manager.io/cluster-issuer: "letsencrypt-prod"
spec:
  ingressClassName: nginx
  tls:
    - hosts:
        - shop.example.com
      secretName: open-hybrid-cloud-tls
  rules:
    - host: shop.example.com
      http:
        paths:
          - path: /
            pathType: Prefix
            backend:
              service:
                name: open-hybrid-cloud
                port:
                  number: 80
\end{lstlisting}

\item \textbf{(Optional) Configure Horizontal Pod Autoscaler.}
\begin{lstlisting}[style=yaml,caption={HorizontalPodAutoscaler},label={lst:k8s-hpa}]
apiVersion: autoscaling/v2
kind: HorizontalPodAutoscaler
metadata:
  name: open-hybrid-cloud
  namespace: open-hybrid-cloud
spec:
  scaleTargetRef:
    apiVersion: apps/v1
    kind: Deployment
    name: open-hybrid-cloud
  minReplicas: 2
  maxReplicas: 6
  metrics:
    - type: Resource
      resource:
        name: cpu
        target:
          type: Utilization
          averageUtilization: 70
\end{lstlisting}

\item \textbf{Apply all manifests and verify.}
\begin{lstlisting}[style=bash]
kubectl apply -f secret.yaml
kubectl apply -f deployment.yaml
kubectl apply -f ingress.yaml
kubectl apply -f hpa.yaml      # optional

kubectl rollout status deployment/open-hybrid-cloud -n open-hybrid-cloud
kubectl get ingress -n open-hybrid-cloud
\end{lstlisting}

\end{enumerate}

\notebox{The polling goroutines that track GitLab pipeline status run
inside each pod. With multiple replicas, advisory locks in PostgreSQL
(\code{pg\_try\_advisory\_lock}) ensure that only one pod polls each
pipeline at a time, preventing duplicate status updates.}

\section{Database Migrations}

Migrations are versioned SQL files in \file{internal/migrations/}.
Run migrations before starting the server:

\begin{lstlisting}[style=bash]
# Run all pending migrations
make migrate

# Or directly
go run ./cmd/migrate
\end{lstlisting}

Migrations are idempotent (\code{IF NOT EXISTS} guards). Re-running is safe.

\section{First Login}

\begin{enumerate}
  \item Navigate to the webshop URL.
  \item Click \textbf{Local Login} (not \textbf{Sign in with Microsoft}).
  \item Enter the email and password from \env{ADMIN\_EMAIL} and
        \env{ADMIN\_PASSWORD}.
  \item Navigate to \textbf{Settings → My Profile} and change the
        default password immediately.
\end{enumerate}

% ─────────────────────────────────────────────────────────────
\chapter{System Configuration}
\label{ch:sysconfig}

\section{GitLab Sources}

Under \textbf{Administration → GitLab Sources}:

\begin{enumerate}
  \item Click \textbf{Add New Source}.
  \item Enter a \textbf{Name} (label), the instance \textbf{URL}, and
        a \textbf{Personal Access Token} with \code{read\_api} scope.
  \item Save. The source is now available when creating environments and
        when browsing repositories for parameter import.
\end{enumerate}

\section{Deployment Environments}

Under \textbf{Administration → Deployment Environments}:

\begin{enumerate}
  \item Click \textbf{Add New Environment}.
  \item Enter a \textbf{Name} (e.g. \textit{Linode Frankfurt Production}),
        select the \textbf{GitLab Source}, and enter the \textbf{Webhook URL}
        and \textbf{Webhook Token}.
  \item Save. The environment becomes available when assigning products.
\end{enumerate}

\notebox{The Webhook URL points to a specific GitLab project pipeline
trigger endpoint, e.g.:\\
\url{https://gitlab.example.com/api/v4/projects/42/ref/main/trigger/pipeline}}

\section{SMTP Configuration}

Under \textbf{Administration → Email} (\route{/admin/smtp}):

Enter host, port, sender address, username, password, and TLS mode.
Click \textbf{Save}. The notification service reloads credentials
immediately without a server restart.

\section{AI Translation}
\label{sec:aitranslation}

Under \textbf{Administration → AI Translation} (\route{/admin/ai-config}):

\begin{enumerate}
  \item Select a \textbf{Provider}: Claude, OpenAI, Azure OpenAI,
        Ollama, or LocalAI.
  \item Enter the \textbf{API endpoint} and \textbf{API key}.
        For Ollama/LocalAI, the endpoint is a local URL and no key
        is required.
  \item Enter the \textbf{model name} (e.g. \code{claude-opus-4-7},
        \code{gpt-4o}, \code{llama3.1}).
  \item Click \textbf{Save}. The translator instance is replaced
        immediately — the next translation request uses the new provider.
\end{enumerate}

\section{Branding}
\label{sec:branding}

Under \textbf{Administration → Shop Design} (\route{/admin/branding}):

\begin{itemize}
  \item \textbf{Shop Name} and \textbf{Subtitle} — shown in the header.
  \item \textbf{Primary Color} — header, footer, navigation
        (default: \code{\#0f172a}).
  \item \textbf{Accent Color} — buttons and call-to-action elements
        (default: \code{\#0ea5e9}).
  \item \textbf{Logo} — PNG or SVG, displayed in the header; replaces
        the shop name text if present.
  \item \textbf{Imprint} — HTML-formatted legal imprint text, shown at
        \route{/impressum}.
\end{itemize}

All branding values are stored in a singleton database row and cached
in-memory with a mutex for read performance.

\section{Currencies}
\label{sec:currencies}

Under \textbf{Administration → Currencies}:

\begin{enumerate}
  \item The \textbf{base currency} (default EUR) is the currency in
        which all product prices are stored.
  \item Optionally configure an exchange rate API key and endpoint.
  \item Click \textbf{Update Rates} to fetch live rates.
  \item Individual rates can be overridden manually for fixed-rate
        environments.
\end{enumerate}

Prices are displayed in the user's locale currency by looking up the
browser locale and applying the stored rate.

% ─────────────────────────────────────────────────────────────
\chapter{User Management}
\label{ch:users}

\section{Roles}

\begin{table}[H]
  \centering
  \caption{User roles and capabilities}
  \begin{tabularx}{\linewidth}{@{}l>{\raggedright\arraybackslash}Xll@{}}
    \toprule
    \textbf{Role} & \textbf{Description} &
      \textbf{Auth method} & \textbf{DB role} \\
    \midrule
    Admin         & Full access; direct ordering; approval & SSO  & \code{admin} \\
    Root    & Catalog \& config; no ordering          & Local & \code{root} \\
    Project Manager  & Orders own infra; approval required     & SSO  & \code{project\_leader} \\
    \bottomrule
  \end{tabularx}
\end{table}

\section{Creating a Local Account}

Under \textbf{Administration → Users}:

\begin{enumerate}
  \item Click \textbf{New User}.
  \item Enter \textbf{Name}, \textbf{Email}, \textbf{Password}, and
        select a \textbf{Role}.
  \item Click \textbf{Save}.
\end{enumerate}

SSO users are created automatically on first login.

\section{Editing Users}

Click \textbf{Edit} next to a user to change name, email, or role.
The password can only be changed by the user themselves under
\textbf{Settings → My Profile}.

\section{Deactivating Users}

Click \textbf{Deactivate} on the user edit page. Deactivated users
cannot log in. Their orders and projects remain visible in the system.

% ─────────────────────────────────────────────────────────────
\chapter{Audit Log}
\label{ch:audit}

The audit log under \route{/audit} is an append-only, tamper-evident
record of all system actions.

\section{Logged Events}

\begin{table}[H]
  \centering
  \caption{Audited actions}
  \begin{tabular}{@{}ll@{}}
    \toprule
    \textbf{Action} & \textbf{Trigger} \\
    \midrule
    \code{order\_placed}      & User submits an order \\
    \code{order\_approved}    & Admin approves \\
    \code{order\_rejected}    & Admin rejects (with comment) \\
    \code{order\_deployed}    & Pipeline completes successfully \\
    \code{order\_failed}      & Pipeline fails \\
    \code{decommission\_started}  & User triggers decommission \\
    \code{decommission\_complete} & Destroy pipeline succeeds \\
    \code{user\_login}        & Successful authentication \\
    \code{user\_created}      & Admin creates a user \\
    \code{config\_changed}    & System configuration updated \\
    \bottomrule
  \end{tabular}
\end{table}

\section{Filtering}

Use the filter form to narrow results by:
\begin{itemize}
  \item \textbf{Date range} (from / to)
  \item \textbf{User}
  \item \textbf{Action type}
\end{itemize}

\section{Export}

Click \textbf{Export CSV} or \textbf{Export PDF} to download the
currently filtered audit log for compliance reporting.

% ─────────────────────────────────────────────────────────────
%  PART IV — DEVELOPER GUIDE
% ─────────────────────────────────────────────────────────────
\part{Developer Guide}
\label{part:dev}

% ─────────────────────────────────────────────────────────────
\chapter{Development Environment}
\label{ch:devenv}

\section{Prerequisites}

\begin{itemize}
  \item Go 1.23+
  \item Node.js 20+ (for Tailwind CSS compilation)
  \item Docker \& Docker Compose (for local PostgreSQL)
  \item \code{golangci-lint} (static analysis — installed via \code{make install-requirements})
  \item \code{pdflatex} or \code{lualatex} (for handbook compilation, optional)
\end{itemize}

On Ubuntu or Manjaro all prerequisites except \code{pdflatex} can be installed
with a single command:

\begin{lstlisting}[style=bash]
make install-requirements
\end{lstlisting}

This detects the native package manager (\code{pacman} or \code{apt-get}),
installs Go, Node.js, npm, Docker, and Docker Compose, and then installs the
Go tools \code{goimports} and \code{golangci-lint} via \code{go install}.
A re-login is required afterwards for the Docker group membership to take effect.

\notebox{\textbf{Ubuntu note:} The \code{golang-go} package in the Ubuntu repositories
  may lag behind the latest Go release. If Go~1.23+ is not available, install it
  manually from \url{https://go.dev/dl/}.}

\section{Quick Start}

\begin{lstlisting}[style=bash]
# Clone and enter the repo
git clone https://github.com/Maximilian-Maag/open-hybrid-cloud.git
cd open-hybrid-cloud

# Install all required tools (Ubuntu / Manjaro)
make install-requirements

# Copy and populate environment
cp .env.example .env
# Edit .env with your local DB credentials

# Start PostgreSQL and the server in one command
make dev

# In another terminal: CSS hot-reload
make css-watch
\end{lstlisting}

\code{make dev} starts Docker Compose (PostgreSQL), runs CSS build, then
starts the Go server with live environment variables from \file{.env}.

\section{Makefile Targets}

\begin{table}[H]
  \centering
  \caption{Makefile targets}
  \begin{tabular}{@{}ll@{}}
    \toprule
    \textbf{Target} & \textbf{Action} \\
    \midrule
    \code{make build}      & Build CSS + Go binary \\
    \code{make run}        & Start server (requires running DB) \\
    \code{make migrate}    & Run database migrations \\
    \code{make css}        & Build Tailwind CSS once \\
    \code{make css-watch}  & Watch and rebuild CSS on change \\
    \code{make test}       & Run all Go tests \\
    \code{make vet}        & Run \code{go vet} \\
    \code{make lint}       & Run \code{golangci-lint} \\
    \code{make install-requirements} & Install system packages + Go tools (Ubuntu/Manjaro) \\
    \code{make docker-build} & Build Docker image \\
    \code{make dev}        & Start DB + server (development) \\
    \code{make dev-down}   & Stop DB + server \\
    \code{make clean}      & Remove build artefacts \\
    \code{make docs}       & Compile the LaTeX handbook to PDF \\
    \code{make e2e}        & Run Playwright end-to-end tests (requires Docker) \\
    \bottomrule
  \end{tabular}
\end{table}

The repository also includes a local smoke test runner in \file{cmd/smoke/}. Run:

\begin{lstlisting}[style=bash]
DATABASE_URL=postgres://postgres:postgres@localhost:5432/infrawebshop?sslmode=disable \
  go run ./cmd/smoke
\end{lstlisting}

This command creates temporary rows and verifies cascading cleanup for product deletion.

% ─────────────────────────────────────────────────────────────
\chapter{Codebase Structure}
\label{ch:codebase}

\section{Directory Layout}

\begin{lstlisting}
open-hybrid-cloud/
+-- cmd/
|   +-- server/         # main.go -- server entry point
|   +-- migrate/        # main.go -- migration runner
|   +-- smoke/          # main.go -- smoke test runner
+-- e2e/                # Playwright end-to-end tests (src/e2e/)
+-- docs/               # Documentation (this handbook)
|   +-- handbook.tex
|   +-- handbook.pdf    # compiled output
+-- internal/
|   +-- aitranslation/  # AI translator interface + backends
|   +-- audit/          # AuditService implementation
|   +-- auth/           # OIDC, session store, password hashing
|   +-- config/         # Config struct loaded from env
|   +-- exchange/       # Currency exchange rate service
|   +-- handler/        # HTTP handlers and route registration
|   +-- i18n/           # 25-language key-value translation map
|   +-- migrations/     # SQL migration files (001_*.sql, ...)
|   +-- model/          # Shared domain model structs
|   +-- notification/   # SMTP notification service
|   +-- repository/     # Repository interfaces
|   |   +-- postgres/   # pgx/v5 implementations
|   +-- service/        # Service interfaces
|       +-- impl/       # Service implementations
+-- ui/
    +-- comp/                   # Shared templ component library
    |   +-- layout.templ        # Full-page layout shell + nav
    |   +-- badge.templ         # Status badges
    |   +-- button.templ        # Button variants (Btn, BtnLink, IconBtn)
    |   +-- card.templ          # Card, CardBody, CardHeader, PageHeader
    |   +-- form.templ          # Field, Input, Textarea, Select, Checkbox
    +-- pages/                  # One package per route group
    |   +-- admin/              # *.templ for all /admin/* pages
    |   +-- approvals/
    |   +-- audit/
    |   +-- auth/
    |   +-- catalog/
    |   +-- home/
    |   +-- infra/
    |   +-- misc/
    |   +-- orders/
    |   +-- projects/
    |   +-- settings/
    +-- static/
    |   +-- css/style.css       # Compiled Tailwind output
    +-- ui.go                   # embed.FS declarations
\end{lstlisting}

\section{Layered Architecture}

The code follows a strict layered architecture with downward-only
dependencies:

\[
\text{Handler} \rightarrow \text{Service} \rightarrow \text{Repository} \rightarrow \text{PostgreSQL}
\]

\begin{description}
  \item[\textbf{Handler layer}] (\file{internal/handler/})
    HTTP handlers only. Read request, call service, render template.
    No business logic. No SQL.
  \item[\textbf{Service layer}] (\file{internal/service/})
    Business rules and orchestration. Calls repositories. Triggers
    notifications, audit writes, webhook dispatches.
    Defined as interfaces in \file{service.go}, implemented in
    \file{impl/}.
  \item[\textbf{Repository layer}] (\file{internal/repository/})
    Data access. Defined as interfaces (one per aggregate root).
    Implemented in \file{postgres/} using pgx. No business logic.
  \item[\textbf{Model layer}] (\file{internal/model/})
    Plain Go structs shared across layers. No methods beyond simple
    helpers.
\end{description}

\section{Template System (templ)}

All pages are authored as \code{.templ} files and compiled to Go by
\code{templ generate ./...}. Each \code{.templ} file produces a
corresponding \code{\_templ.go} file which is committed alongside the
source.

Page components receive a typed view struct:
\begin{lstlisting}[style=go]
// ui/pages/orders/orders.templ
templ OrderList(vd view.OrderListView) {
    @comp.Layout(vd.PageData) {
        // page content -- type-checked at compile time
    }
}
\end{lstlisting}

Handlers assemble the view struct and call \code{renderTempl}:
\begin{lstlisting}[style=go]
func (h *Handler) orderList(w http.ResponseWriter, r *http.Request) {
    orders, _ := h.orders.ListByUser(r.Context(), sess.UserID)
    renderTempl(w, r, orderpages.OrderList(view.OrderListView{
        PageData: h.buildPageData(w, r),
        Orders:   orders,
    }))
}
\end{lstlisting}

\code{buildPageData} assembles the common \code{view.PageData} struct
providing:
\begin{description}
  \item[\code{.Lang}] User's active language code (e.g.\ \code{"de"}).
  \item[\code{.Brand}] Branding values (colours, shop name, logo flag).
  \item[\code{.Session}] Current user session (name, role, email).
  \item[\code{.Flash}] One-time flash message (success/error).
  \item[\code{.SearchQuery}] Current catalog search term from the URL.
\end{description}

Translations are called directly in templ files:
\begin{lstlisting}[style=go]
{ i18n.T("orders.title", vd.Lang) }  // translated string
{ string(o.Status) }                  // named type requires cast
\end{lstlisting}

\section{Design System}
\label{sec:design-system}

All UI is built from a small, self-contained component library under
\file{src/ui/comp/}. Components are plain templ functions — no
framework, no runtime dependencies.

\subsection*{Design Tokens}

Two CSS custom properties drive every coloured surface:

\begin{description}
  \item[\code{var(--bp)}] Brand primary colour (default \code{\#0f172a},
        dark slate). Used for header, navigation, footer, active
        highlights, and price text.
  \item[\code{var(--bs)}] Brand secondary / accent colour (default
        \code{\#0ea5e9}, sky blue). Used for CTA buttons, active language
        badges, and focus rings.
\end{description}

The values are injected by \code{comp.Layout} as inline CSS custom
properties on \code{<html>}. Every component should reference these
variables rather than hardcoding colours:

\begin{lstlisting}[style=go]
<!-- correct -->
<div style="background-color:var(--bp)">...</div>
<a style="color:var(--bs)">...</a>

<!-- wrong: breaks custom branding -->
<div class="bg-[#0f172a]">...</div>
\end{lstlisting}

\subsection*{Layout Shell (\texttt{comp.Layout})}

Every page is wrapped in \code{comp.Layout}:

\begin{lstlisting}[style=go]
templ MyPage(vd view.MyView) {
    @comp.Layout(vd.PageData) {
        // page content here
    }
}
\end{lstlisting}

\code{comp.Layout} renders: \texttt{<head>} with meta tags and stylesheets,
sticky header with brand logo / search bar / user menu / language
picker, the top navigation bar with role-based links, a flash banner
slot, the \texttt{<main>} content area (2XL max-width, horizontal
padding), and the footer. Nothing else should set \code{<html>},
\code{<head>}, or \code{<body>}.

\subsection*{Page Structure}

\begin{description}
  \item[\code{comp.PageHeader(title, backHref)}]
        Full-width page title row with an optional back arrow link.
        Use at the top of every dedicated page.
  \item[\code{comp.PageHeaderAction(title, backHref, action)}]
        Same as above but with an action slot on the right (e.g.\ a
        primary button).
  \item[\code{comp.Section(title)}]
        A titled content group with a subtle separator. Use to divide
        a page into logical parts.
  \item[\code{comp.EmptyState(message)}]
        Centred placeholder message for empty lists or zero results.
\end{description}

\begin{lstlisting}[style=go]
@comp.PageHeaderAction("Bestellungen", "/", action) {
    @comp.BtnLink("Neue Bestellung", "/catalog",
                  comp.VPrimary, comp.SzMD)
}
@comp.Section("Offene Bestellungen") {
    if len(orders) == 0 {
        @comp.EmptyState("Keine Bestellungen vorhanden.")
    }
    // list rows...
}
\end{lstlisting}

\subsection*{Cards}

\begin{description}
  \item[\code{comp.Card()}]
        White surface with border and subtle shadow. Use as a generic
        content container.
  \item[\code{comp.CardBody()}]
        Adds consistent padding inside a \code{Card}.
  \item[\code{comp.CardHeader(title)}]
        A titled header strip for a card.
\end{description}

\begin{lstlisting}[style=go]
@comp.Card() {
    @comp.CardHeader("Details") {}
    @comp.CardBody() {
        // form fields, table, prose, etc.
    }
}
\end{lstlisting}

\subsection*{Buttons}

\begin{description}
  \item[\code{comp.Btn(label, variant, size, templ.Attributes)}]
        A \code{<button>} element. Pass extra HTML attributes (e.g.\
        \code{hx-post}, \code{disabled}) via the fourth argument.
  \item[\code{comp.BtnLink(label, href, variant, size)}]
        An \code{<a>} element styled as a button. Use for navigation
        CTAs.
  \item[\code{comp.IconBtn(variant, size, templ.Attributes)}]
        Square icon button; children supply the icon SVG.
  \item[\code{comp.BtnClass(variant, size)}]
        Returns just the Tailwind class string. Use when you need to
        apply button styling to an element not covered by the
        components above (e.g.\ an HTMX-powered \code{<button>} inside
        a templ \code{children...} slot).
\end{description}

\textbf{Variants:}

\begin{tabular}{ll}
\code{comp.VPrimary}   & Filled, uses \code{var(--bp)} background — main CTAs. \\
\code{comp.VSecondary} & Outlined border button — secondary actions. \\
\code{comp.VGhost}     & Transparent, text-only — low-emphasis actions. \\
\code{comp.VDanger}    & Red filled — destructive actions (delete, reject). \\
\end{tabular}

\textbf{Sizes:}

\begin{tabular}{ll}
\code{comp.SzXS} & Extra small — inline or table-row actions. \\
\code{comp.SzSM} & Small — secondary actions, compact layouts. \\
\code{comp.SzMD} & Medium (default) — primary page-level CTAs. \\
\end{tabular}

\begin{lstlisting}[style=go]
// Primary CTA
@comp.BtnLink("Jetzt bestellen", "/catalog/"+id,
              comp.VPrimary, comp.SzMD)

// Danger action with HTMX
@comp.Btn("Ablehnen", comp.VDanger, comp.SzSM,
          templ.Attributes{"hx-delete": "/orders/"+id,
                           "hx-confirm": "Wirklich ablehnen?"})

// Icon button (custom SVG inside)
@comp.IconBtn(comp.VGhost, comp.SzXS,
              templ.Attributes{"aria-label": "Bearbeiten"}) {
    <svg .../>
}
\end{lstlisting}

\subsection*{Badges}

\begin{description}
  \item[\code{comp.Badge(label, color)}]
        A small inline pill. Use \code{comp.BadgeGreen}, \code{comp.BadgeRed},
        \code{comp.BadgeYellow}, \code{comp.BadgeBlue}, or
        \code{comp.BadgeGray} for the \code{color} argument.
  \item[\code{comp.StatusBadge(status)}]
        Convenience wrapper that maps an order/resource status string
        to the appropriate colour via \code{comp.StatusBadgeColor}.
        No need to branch on status in the template.
\end{description}

\begin{lstlisting}[style=go]
// Generic badge
@comp.Badge("Aktiv", comp.BadgeGreen)
@comp.Badge("Fehler", comp.BadgeRed)

// Status-aware badge (recommended for orders)
@comp.StatusBadge(string(order.Status))
\end{lstlisting}

Status colour mapping (via \code{comp.StatusBadgeColor}):

\begin{tabular}{ll}
\code{active}, \code{approved}, \code{completed} & Green \\
\code{pending}                                    & Yellow \\
\code{failed}, \code{rejected}                    & Red \\
\code{provisioning}, \code{decommissioning}       & Blue \\
Everything else                                   & Gray \\
\end{tabular}

\subsection*{Forms}

All form fields use the components in \file{ui/comp/form.templ} for
consistent label alignment, spacing, and required-marker rendering.

\begin{description}
  \item[\code{comp.Field(label, name, required)}]
        A \code{<label>} + slot wrapper. Place an \code{Input},
        \code{Select}, or \code{Textarea} inside it.
  \item[\code{comp.Input(name, type, placeholder, value, attrs)}]
        Styled \code{<input>}. Pass extra attributes (e.g.\
        \code{hx-get}, \code{min}, \code{step}) via the last argument.
  \item[\code{comp.Textarea(name, placeholder, value, rows, attrs)}]
        Styled \code{<textarea>}.
  \item[\code{comp.Select(name, attrs)}]
        Styled \code{<select>} wrapper; children are \code{<option>}
        elements written inline.
  \item[\code{comp.Checkbox(name, label, checked)}]
        A labelled checkbox with correct \code{for}/\code{id} wiring.
\end{description}

\begin{lstlisting}[style=go]
<form method="POST" action="/admin/products">
    @comp.Field("Produktname", "name", true) {
        @comp.Input("name", "text", "z.B. VM-Platform",
                    product.Name, nil)
    }
    @comp.Field("Beschreibung", "description", false) {
        @comp.Textarea("description", "", product.Description,
                       4, nil)
    }
    @comp.Field("Kategorie", "category_id", true) {
        @comp.Select("category_id", nil) {
            for _, c := range categories {
                <option value={ fmt.Sprint(c.ID) }
                        selected?={ c.ID == product.CategoryID }>
                    { c.Name }
                </option>
            }
        }
    }
    @comp.Field("Aktiv", "active", false) {
        @comp.Checkbox("active", "Produkt ist sichtbar",
                       product.Active)
    }
    @comp.Btn("Speichern", comp.VPrimary, comp.SzMD, nil)
</form>
\end{lstlisting}

\subsection*{Flash Messages}

Flash messages are set server-side via \code{redirectWithFlash} and
rendered automatically by \code{comp.Layout} from \code{pd.Flash}.
HTMX responses that want to show a flash message use the
\code{HX-Trigger} response header instead:

\begin{lstlisting}[style=go]
// In a handler that returns an HTMX partial:
w.Header().Set("HX-Trigger", `{"showFlash":{"kind":"success",
    "message":"Gespeichert"}}`)
\end{lstlisting}

\subsection*{Component Conventions}

\begin{itemize}
  \item \textbf{Never hardcode colours.} Always use \code{var(--bp)},
        \code{var(--bs)}, or Tailwind's neutral palette
        (\code{slate-*}). Hardcoded hex values break custom branding.
  \item \textbf{Use \code{comp.VPrimary} for the single most important
        action} on a page. Use \code{comp.VSecondary} or
        \code{comp.VGhost} for everything else.
  \item \textbf{No JavaScript.} Interactive disclosure (menus, modals,
        accordions) uses native \code{<details>/<summary>}.
        Server-side partial updates use HTMX attributes. Never add
        \code{<script>} tags to component files.
  \item \textbf{No inline \code{style} except for brand tokens.}
        Arbitrary colours, sizes, and spacing belong in Tailwind
        utility classes, not \code{style=""} attributes.
  \item \textbf{Prefer \code{comp.StatusBadge} over manual branching.}
        The mapping is maintained centrally; adding a new status only
        requires updating \code{comp.StatusBadgeColor}.
\end{itemize}

\section{Adding Translations}

All UI strings live in \file{internal/i18n/i18n.go} as a
\code{map[string]map[string]string}. To add a new key:

\begin{lstlisting}[style=go]
// In translations map:
"my.new.key": {
    "en": "English text",
    "de": "Deutscher Text",
    "fr": "Texte francais",
    // ... all 25 language codes
},
\end{lstlisting}

Use in templates with \code{\{\{t "my.new.key" .Lang\}\}}.

\section{Database Migrations}
\label{sec:dbmigrations}

Migration files follow the naming pattern
\file{NNN\_description.sql} and are executed in alphabetical order.
Write migrations defensively:

\begin{lstlisting}[style=sql]
ALTER TABLE products
  ADD COLUMN IF NOT EXISTS image_mime TEXT NOT NULL DEFAULT 'image/jpeg';

CREATE TABLE IF NOT EXISTS app_config (
  id INT PRIMARY KEY DEFAULT 1 CHECK (id = 1),
  smtp_host TEXT NOT NULL DEFAULT ''
  -- ...
);
\end{lstlisting}

\warnbox{Never modify a migration that has already been applied to
production. Always create a new migration file for schema changes.}

% ─────────────────────────────────────────────────────────────
\chapter{Testing}
\label{ch:testing}

The project uses three complementary test layers.  All three are invoked
automatically in CI; locally the most common commands are
\code{make test} (fast, no Docker needed) and \code{make e2e} (full
browser stack, requires Docker).

% ─────────────────────────────────────────────────────────────
\section{Unit Tests}
\label{sec:unit-tests}

Unit tests live next to the code they test (\file{*\_test.go}) and use
Go's standard \code{testing} package.  They cover:

\begin{itemize}
  \item \textbf{Service layer} (\file{internal/service/impl/}) ---
        all service methods are tested with in-memory stubs that
        implement the repository interfaces.  No database, no network.
  \item \textbf{Handler helpers} (\file{internal/handler/}) ---
        language detection (\code{parseAcceptLanguage},
        \code{detectLang}) and the login rate-limiter are tested with
        direct function calls.
  \item \textbf{Polling worker} (\file{internal/polling/}) ---
        \code{extractProjectID} is tested with table-driven cases.
\end{itemize}

Run unit tests:
\begin{lstlisting}[style=bash]
make test          # runs go test ./...
make vet           # go vet (zero warnings required)
make lint          # golangci-lint
\end{lstlisting}

% ─────────────────────────────────────────────────────────────
\section{Integration Tests (testcontainers-go)}
\label{sec:integration-tests}

Repository-layer tests in \file{internal/repository/postgres/} spin up
a real \textbf{PostgreSQL 16 Alpine} container via
\href{https://golang.testcontainers.org}{testcontainers-go} and run all
migrations before the first test.

\subsection*{TestMain}

\begin{lstlisting}[style=go]
// testmain_test.go
func TestMain(m *testing.M) {
    ctr, err := tcpostgres.Run(ctx, "postgres:16-alpine",
        tcpostgres.WithDatabase("testdb"),
        testcontainers.WithWaitStrategy(
            wait.ForLog("database system is ready to accept connections").
                WithOccurrence(2).WithStartupTimeout(60*time.Second),
        ),
    )
    // runs migrations, opens pgxpool
    os.Exit(m.Run())
}
\end{lstlisting}

\subsection*{Test isolation}

Every test that writes data calls \code{resetDB(t)} first, which
truncates all data tables and restarts identity sequences:

\begin{lstlisting}[style=go]
func resetDB(t *testing.T) {
    _, err := testPool.Exec(ctx,
        "TRUNCATE audit_log, orders, products, ... RESTART IDENTITY CASCADE")
}
\end{lstlisting}

\subsection*{Fixture helper}

Tests that need FK-dependent data call \code{newFixture(t)}, which
creates the full dependency chain in one call:

\begin{lstlisting}
gitlab_source -> deployment_environment -> user
             -> category -> product -> project
\end{lstlisting}

Integration tests require Docker; if the container cannot start the
test binary exits with code~0 (skip, not fail) so CI stays green on
environments without Docker.

% ─────────────────────────────────────────────────────────────
\section{End-to-End Tests with Playwright}
\label{sec:e2e-tests}

End-to-end tests live in \file{src/e2e/} and drive a real
\textbf{Chromium} browser via
\href{https://github.com/playwright-community/playwright-go}{playwright-go}.
The full application stack --- PostgreSQL, all migrations, all service
wiring --- is started in-process for each test run.

\subsection*{Architecture}

\begin{figure}[H]
\centering
\begin{tikzpicture}[
  box/.style={rectangle, rounded corners=4pt, draw=ohc-blue!50,
              fill=ohc-blue!8, minimum width=3.0cm, minimum height=0.9cm,
              align=center, font=\small},
  arr/.style={->, >=Stealth, thick, ohc-blue!60},
  node distance=0.6cm and 1.4cm
]
  \node[box] (pg)  {Testcontainers\\PostgreSQL};
  \node[box, right=of pg] (srv) {\texttt{httptest}\\Server};
  \node[box, right=of srv] (pw)  {Playwright\\Chromium};
  \node[box, below=of srv] (wh)  {Mock GitLab\\Webhook Server};
  \draw[arr] (pg)  -- node[above,font=\tiny] {pool} (srv);
  \draw[arr] (srv) -- node[above,font=\tiny] {HTTP} (pw);
  \draw[arr] (srv) -- node[left,font=\tiny]  {POST} (wh);
\end{tikzpicture}
\caption{E2E test infrastructure}
\end{figure}

\begin{description}
  \item[\textbf{Testcontainers PostgreSQL}]
        A real \code{postgres:16-alpine} container is started by
        \code{TestMain}.  All 12 migrations run against it and the
        admin user is bootstrapped (email \code{admin@e2etest.local},
        password \code{e2eAdmin123!}).
  \item[\textbf{\texttt{app.New()}}]
        The server wiring function from \file{internal/app/wire.go}
        assembles the full dependency graph (repos, services, handlers)
        and returns an \code{http.Handler}.
  \item[\textbf{\texttt{httptest.NewServer}}]
        Wraps the handler in a local HTTP server on a random port.
        Playwright's \code{BaseURL} is set to this address.
  \item[\textbf{Mock GitLab webhook server}]
        Approving an order triggers a GitLab pipeline via HTTP POST.
        A second \code{httptest.Server} intercepts these calls and
        returns \code{\{"id":42\}} so the approval flow completes
        without a real GitLab instance.
  \item[\textbf{Chromium (headless)}]
        One browser is launched for the entire test run.  Each test
        gets its own \emph{browser context} (isolated cookie jar) via
        \code{newPage(t)}.
\end{description}

\subsection*{Test file overview}

\begin{table}[H]
  \centering
  \caption{E2E test files}
  \begin{tabular}{@{}lll@{}}
    \toprule
    \textbf{File} & \textbf{Tests} & \textbf{What is verified} \\
    \midrule
    \file{auth\_test.go}     & 3 & Login success, invalid credentials, logout dropdown \\
    \file{approval\_test.go} & 3 & Empty list, Approve button, Reject button \\
    \file{catalog\_test.go}  & 3 & Page loads, empty state, product navigation \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection*{Shared helpers}

\begin{description}
  \item[\code{newPage(t)}]
        Creates a fresh browser context and page; the context is closed
        in \code{t.Cleanup}.  Each test gets an empty cookie jar, so
        sessions never leak between tests.
  \item[\code{loginAs(t, page, email, password)}]
        Navigates to \route{/login}, fills both fields, clicks
        \emph{Submit}, and waits for the redirect to \route{/}.
  \item[\code{resetData(t)}]
        Truncates all data tables (except \code{users}) with
        \code{RESTART IDENTITY CASCADE}, so the bootstrapped admin
        user survives across tests.
  \item[\code{seedPendingOrder(t)}]
        Inserts the full FK chain (gitlab\_source, environment,
        category, product, project, order) with \code{status =
        'pending\_approval'}.  Uses \code{webhookBaseURL} so the mock
        server intercepts the approval webhook call.
\end{description}

\subsection*{Key selector conventions}

Because approvals use plain HTML \code{<form>} elements (no HTMX),
tests use stable \textbf{action-attribute selectors}:

\begin{lstlisting}[style=go]
// approve button for a specific order
approveForm := page.Locator(
    fmt.Sprintf(`form[action="/approvals/%d/approve"]`, fix.orderID))
approveForm.Locator(`button[type="submit"]`).Click()

// reject form is inside a <details> -- open summary first
page.Locator(`details.mt-4 > summary`).First().Click()
noteInput := page.Locator(`input[name="note"]`)
noteInput.WaitFor()            // waits until visible
noteInput.Fill("reason")
\end{lstlisting}

After a form submit the 303~redirect reloads the same URL.
\code{WaitForLoadState(NetworkIdle)} is used instead of
\code{WaitForURL} (which would return immediately because the URL
does not change).

\subsection*{Running the tests}

\begin{lstlisting}[style=bash]
# Headless (CI / default)
make e2e

# Headed -- watch the browser while tests run
E2E_HEADED=true make e2e

# First run downloads Chromium (~170 MB) into ~/.cache/ms-playwright/
\end{lstlisting}

If Docker is unavailable the test binary exits with code~0 (skip, not
fail), consistent with the integration test policy.

\subsection*{Adding a new E2E test}

\begin{enumerate}
  \item Call \code{resetData(t)} at the start if the test writes data.
  \item Use \code{newPage(t)} to get an isolated page.
  \item Use \code{loginAs} to authenticate if needed.
  \item Prefer \code{form[action="..."]} and \code{input[name="..."]}
        selectors over CSS classes (classes change; actions rarely do).
  \item After a form submit call
        \code{page.WaitForLoadState(NetworkIdle)} before asserting.
\end{enumerate}

% ─────────────────────────────────────────────────────────────
\chapter{Database Schema}
\label{ch:db-schema}

The schema is built by 12 sequential migrations (see
Section~\ref{sec:dbmigrations}).  The table below shows the
\textbf{current effective schema} — i.e.\ the cumulative result of all
migrations.

% ─────────────────────────────────────────────────────────────
\section{Table Overview}
\label{sec:schema-overview}

\begin{table}[H]
  \centering
  \caption{All database tables}
  \begin{tabular}{@{}lp{9cm}@{}}
    \toprule
    \textbf{Table} & \textbf{Purpose} \\
    \midrule
    \code{users}                    & User accounts (local + SSO) with role-based access \\
    \code{categories}               & Product catalogue categories \\
    \code{products}                 & Infrastructure products offered in the catalogue \\
    \code{product\_translations}    & Multi-language name + description per product \\
    \code{parameters}               & Configurable inputs for global/category/product scope \\
    \code{gitlab\_sources}          & GitLab instance credentials (URL + access token) \\
    \code{deployment\_environments} & Named environments linked to a GitLab source \\
    \code{product\_environments}    & Junction: which products are available in which environment (with price) \\
    \code{product\_webhooks}        & Optional per-product pipeline trigger overrides \\
    \code{cost\_centers}            & Billing cost centres referenced by projects and orders \\
    \code{projects}                 & User-owned projects that group orders \\
    \code{orders}                   & Individual infrastructure provisioning requests \\
    \code{infrastructure\_elements} & Deployed instances tracked per order \\
    \code{audit\_log}               & Append-only log of significant user actions \\
    \code{exchange\_rates}          & Cached currency conversion rates \\
    \code{branding}                 & Single-row branding config (logo, colours, texts) \\
    \code{app\_config}              & Single-row application config (SMTP, AI) \\
    \bottomrule
  \end{tabular}
\end{table}

% ─────────────────────────────────────────────────────────────
\section{Detailed Schema}
\label{sec:schema-detail}

Each table is described with its columns (post all migrations), primary
key, foreign keys, and notable constraints.

\subsection*{\texttt{users}}

\begin{table}[H]
  \centering\small
  \begin{tabular}{@{}llll@{}}
    \toprule
    \textbf{Column} & \textbf{Type} & \textbf{Default} & \textbf{Notes} \\
    \midrule
    \code{id}            & BIGSERIAL & --- & PK \\
    \code{email}         & TEXT      & --- & NOT NULL, UNIQUE \\
    \code{name}          & TEXT      & --- & NOT NULL \\
    \code{role}          & TEXT      & --- & CHECK: \code{admin}, \code{project\_leader}, \code{root} \\
    \code{sso\_sub}      & TEXT      & NULL & UNIQUE; set for Entra ID accounts \\
    \code{password\_hash}& TEXT      & NULL & set for local accounts \\
    \code{active}        & BOOLEAN   & TRUE & soft-disable without deletion \\
    \code{created\_at}   & TIMESTAMPTZ & NOW() & \\
    \bottomrule
  \end{tabular}
\end{table}

\noindent\textbf{Constraint:} \code{sso\_sub IS NOT NULL OR password\_hash IS NOT NULL}
(every account must have at least one credential).

\subsection*{\texttt{categories}}

\begin{table}[H]
  \centering\small
  \begin{tabular}{@{}llll@{}}
    \toprule
    \textbf{Column} & \textbf{Type} & \textbf{Default} & \textbf{Notes} \\
    \midrule
    \code{id}            & BIGSERIAL & --- & PK \\
    \code{name}          & TEXT      & --- & NOT NULL \\
    \code{display\_order}& INT       & 0   & controls sidebar sort order \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection*{\texttt{products}}

\begin{table}[H]
  \centering\small
  \begin{tabular}{@{}llll@{}}
    \toprule
    \textbf{Column} & \textbf{Type} & \textbf{Default} & \textbf{Notes} \\
    \midrule
    \code{id}           & BIGSERIAL & ---  & PK \\
    \code{category\_id} & BIGINT    & ---  & NOT NULL, FK \textrightarrow{} \code{categories(id)} ON DELETE CASCADE \\
    \code{base\_language}& TEXT     & \code{'de'} & fallback language for translations \\
    \code{image}        & BYTEA     & NULL & product image stored inline \\
    \code{created\_at}  & TIMESTAMPTZ & NOW() & \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection*{\texttt{product\_translations}}

\begin{table}[H]
  \centering\small
  \begin{tabular}{@{}llll@{}}
    \toprule
    \textbf{Column} & \textbf{Type} & \textbf{Default} & \textbf{Notes} \\
    \midrule
    \code{product\_id}    & BIGINT & --- & PK, FK \textrightarrow{} \code{products(id)} ON DELETE CASCADE \\
    \code{language\_code} & TEXT   & --- & PK, e.g.\ \code{de}, \code{en}, \code{fr} \\
    \code{name}           & TEXT   & --- & NOT NULL \\
    \code{description}    & TEXT   & \code{''} & NOT NULL \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection*{\texttt{parameters}}

\begin{table}[H]
  \centering\small
  \begin{tabular}{@{}llll@{}}
    \toprule
    \textbf{Column} & \textbf{Type} & \textbf{Default} & \textbf{Notes} \\
    \midrule
    \code{id}             & BIGSERIAL & --- & PK \\
    \code{scope}          & TEXT      & --- & CHECK: \code{global}, \code{category}, \code{product} \\
    \code{scope\_id}      & BIGINT    & 0   & ID of the scoped entity (0 for global) \\
    \code{environment\_id}& BIGINT    & 0   & 0 = applies to all environments \\
    \code{name}           & TEXT      & --- & NOT NULL; variable name passed to pipeline \\
    \code{type}           & TEXT      & --- & CHECK: \code{string}, \code{number}, \code{bool}, \code{dropdown} \\
    \code{description}    & TEXT      & \code{''} & \\
    \code{default\_value} & TEXT      & \code{''} & \\
    \code{required}       & BOOLEAN   & FALSE & \\
    \code{sensitive}      & BOOLEAN   & FALSE & renders as \code{type="password"} in UI \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection*{\texttt{gitlab\_sources}}

\begin{table}[H]
  \centering\small
  \begin{tabular}{@{}llll@{}}
    \toprule
    \textbf{Column} & \textbf{Type} & \textbf{Default} & \textbf{Notes} \\
    \midrule
    \code{id}           & BIGSERIAL & --- & PK \\
    \code{name}         & TEXT      & --- & NOT NULL; human-readable label \\
    \code{url}          & TEXT      & --- & NOT NULL; GitLab base URL \\
    \code{access\_token}& TEXT      & --- & NOT NULL; stored in plain text \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection*{\texttt{deployment\_environments}}

\begin{table}[H]
  \centering\small
  \begin{tabular}{@{}llll@{}}
    \toprule
    \textbf{Column} & \textbf{Type} & \textbf{Default} & \textbf{Notes} \\
    \midrule
    \code{id}                & BIGSERIAL & ---       & PK \\
    \code{name}              & TEXT      & ---       & NOT NULL \\
    \code{description}       & TEXT      & \code{''} & \\
    \code{gitlab\_source\_id}& BIGINT    & ---       & NOT NULL, FK \textrightarrow{} \code{gitlab\_sources(id)} \\
    \code{webhook\_url}      & TEXT      & ---       & NOT NULL; GitLab trigger URL \\
    \code{webhook\_token}    & TEXT      & ---       & NOT NULL; pipeline trigger token \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection*{\texttt{product\_environments}}

Junction table linking products to environments with pricing.

\begin{table}[H]
  \centering\small
  \begin{tabular}{@{}llll@{}}
    \toprule
    \textbf{Column} & \textbf{Type} & \textbf{Default} & \textbf{Notes} \\
    \midrule
    \code{product\_id}        & BIGINT        & ---          & PK, FK \textrightarrow{} \code{products(id)} CASCADE \\
    \code{environment\_id}    & BIGINT        & ---          & PK, FK \textrightarrow{} \code{deployment\_environments(id)} \\
    \code{price}              & NUMERIC(12,2) & 0            & monthly price \\
    \code{currency}           & TEXT          & \code{'EUR'} & ISO 4217 code \\
    \code{cost\_center\_mode} & TEXT          & \code{'project'} & CHECK: \code{project}, \code{select}, \code{overhead} \\
    \code{forced\_cost\_center}& BOOLEAN      & FALSE        & locks cost centre selection in order form \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection*{\texttt{product\_webhooks}}

Optional per-product pipeline overrides; if rows exist for a
product+environment pair they replace the environment's default
\code{webhook\_url}.  Multiple rows are fired in ascending
\code{exec\_order}.

\begin{table}[H]
  \centering\small
  \begin{tabular}{@{}llll@{}}
    \toprule
    \textbf{Column} & \textbf{Type} & \textbf{Default} & \textbf{Notes} \\
    \midrule
    \code{id}             & BIGSERIAL & ---       & PK \\
    \code{product\_id}    & BIGINT    & ---       & NOT NULL, FK \textrightarrow{} \code{products(id)} CASCADE \\
    \code{environment\_id}& BIGINT    & ---       & NOT NULL, FK \textrightarrow{} \code{deployment\_environments(id)} \\
    \code{name}           & TEXT      & ---       & NOT NULL; descriptive label \\
    \code{webhook\_url}   & TEXT      & ---       & NOT NULL \\
    \code{webhook\_token} & TEXT      & ---       & NOT NULL \\
    \code{exec\_order}    & INT       & 0         & ascending; ties fire concurrently \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection*{\texttt{cost\_centers}}

\begin{table}[H]
  \centering\small
  \begin{tabular}{@{}llll@{}}
    \toprule
    \textbf{Column} & \textbf{Type} & \textbf{Default} & \textbf{Notes} \\
    \midrule
    \code{id}    & BIGSERIAL & ---  & PK \\
    \code{code}  & TEXT      & ---  & NOT NULL, UNIQUE; billing code \\
    \code{name}  & TEXT      & ---  & NOT NULL \\
    \code{active}& BOOLEAN   & TRUE & inactive centres are hidden in UI \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection*{\texttt{projects}}

\begin{table}[H]
  \centering\small
  \begin{tabular}{@{}llll@{}}
    \toprule
    \textbf{Column} & \textbf{Type} & \textbf{Default} & \textbf{Notes} \\
    \midrule
    \code{id}             & BIGSERIAL   & ---   & PK \\
    \code{name}           & TEXT        & ---   & NOT NULL \\
    \code{description}    & TEXT        & \code{''} & \\
    \code{owner\_id}      & BIGINT      & ---   & NOT NULL, FK \textrightarrow{} \code{users(id)} \\
    \code{cost\_center\_id}& BIGINT     & NULL  & FK \textrightarrow{} \code{cost\_centers(id)} \\
    \code{created\_at}    & TIMESTAMPTZ & NOW() & \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection*{\texttt{orders}}

\begin{table}[H]
  \centering\small
  \begin{tabular}{@{}llll@{}}
    \toprule
    \textbf{Column} & \textbf{Type} & \textbf{Default} & \textbf{Notes} \\
    \midrule
    \code{id}             & BIGSERIAL   & ---     & PK \\
    \code{project\_id}    & BIGINT      & ---     & NOT NULL, FK \textrightarrow{} \code{projects(id)} CASCADE \\
    \code{product\_id}    & BIGINT      & ---     & NOT NULL, FK \textrightarrow{} \code{products(id)} CASCADE \\
    \code{environment\_id}& BIGINT      & ---     & NOT NULL, FK \textrightarrow{} \code{deployment\_environments(id)} \\
    \code{user\_id}       & BIGINT      & ---     & NOT NULL, FK \textrightarrow{} \code{users(id)} \\
    \code{status}         & TEXT        & \code{'pending\_approval'} & see lifecycle below \\
    \code{parameters}     & JSONB       & \code{'\{\}'} & key/value map; passed to pipeline \\
    \code{cost\_center\_id}& BIGINT     & NULL    & FK \textrightarrow{} \code{cost\_centers(id)} \\
    \code{rejection\_note}& TEXT        & \code{''} & filled on rejection \\
    \code{pipeline\_id}   & JSONB       & \code{'[]'} & array of GitLab pipeline IDs \\
    \code{created\_at}    & TIMESTAMPTZ & NOW()   & \\
    \code{updated\_at}    & TIMESTAMPTZ & NOW()   & \\
    \bottomrule
  \end{tabular}
\end{table}

\noindent\textbf{Status lifecycle:}
\code{pending\_approval} \textrightarrow{} \code{approved} / \code{rejected}
\textrightarrow{} \code{provisioning} \textrightarrow{} \code{completed} / \code{failed}
\textrightarrow{} \code{decommissioning} \textrightarrow{} \code{decommissioned}.

\subsection*{\texttt{infrastructure\_elements}}

One row per deployed pipeline; created when an order is approved.

\begin{table}[H]
  \centering\small
  \begin{tabular}{@{}llll@{}}
    \toprule
    \textbf{Column} & \textbf{Type} & \textbf{Default} & \textbf{Notes} \\
    \midrule
    \code{id}             & BIGSERIAL   & ---         & PK \\
    \code{order\_id}      & BIGINT      & ---         & NOT NULL, FK \textrightarrow{} \code{orders(id)} \\
    \code{project\_id}    & BIGINT      & ---         & NOT NULL, FK \textrightarrow{} \code{projects(id)} CASCADE \\
    \code{environment\_id}& BIGINT      & ---         & NOT NULL, FK \textrightarrow{} \code{deployment\_environments(id)} \\
    \code{product\_id}    & BIGINT      & ---         & NOT NULL, FK \textrightarrow{} \code{products(id)} CASCADE \\
    \code{status}         & TEXT        & \code{'provisioning'} & mirrors order status values \\
    \code{parameters}     & JSONB       & \code{'\{\}'} & copy of order parameters at deploy time \\
    \code{pipeline\_id}   & JSONB       & \code{'[]'} & tracked pipeline IDs \\
    \code{outputs}        & JSONB       & \code{'\{\}'} & key/value map of OpenTofu outputs \\
    \code{deployed\_at}   & TIMESTAMPTZ & NOW()       & \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection*{\texttt{audit\_log}}

Append-only; rows are never updated or deleted.

\begin{table}[H]
  \centering\small
  \begin{tabular}{@{}llll@{}}
    \toprule
    \textbf{Column} & \textbf{Type} & \textbf{Default} & \textbf{Notes} \\
    \midrule
    \code{id}         & BIGSERIAL   & ---       & PK \\
    \code{user\_id}   & BIGINT      & ---       & NOT NULL, FK \textrightarrow{} \code{users(id)} \\
    \code{action}     & TEXT        & ---       & NOT NULL; e.g.\ \code{order.created} \\
    \code{entity\_id} & BIGINT      & ---       & NOT NULL; PK of the referenced entity \\
    \code{details}    & TEXT        & \code{''} & extra context (e.g.\ rejection note) \\
    \code{created\_at}& TIMESTAMPTZ & NOW()     & \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection*{\texttt{exchange\_rates}}

\begin{table}[H]
  \centering\small
  \begin{tabular}{@{}llll@{}}
    \toprule
    \textbf{Column} & \textbf{Type} & \textbf{Default} & \textbf{Notes} \\
    \midrule
    \code{currency\_code} & TEXT          & --- & PK; ISO 4217, e.g.\ \code{EUR} \\
    \code{rate}           & NUMERIC(18,6) & --- & NOT NULL; relative to base currency (EUR = 1.0) \\
    \code{updated\_at}    & TIMESTAMPTZ   & NOW() & refreshed via \route{POST /admin/currencies/refresh} \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection*{\texttt{branding}}

Singleton row (\code{id = 1}).  Written via \route{POST /admin/branding}.

\begin{table}[H]
  \centering\small
  \begin{tabular}{@{}llll@{}}
    \toprule
    \textbf{Column} & \textbf{Type} & \textbf{Default} & \textbf{Notes} \\
    \midrule
    \code{id}             & INT   & 1                    & PK, CHECK (id = 1) \\
    \code{logo\_data}     & BYTEA & NULL                 & uploaded logo image \\
    \code{logo\_mime}     & TEXT  & \code{'image/png'}   & MIME type of the logo \\
    \code{primary\_color} & TEXT  & \code{'\#0f172a'}    & \code{var(--bp)} CSS token \\
    \code{secondary\_color}& TEXT & \code{'\#0ea5e9'}    & \code{var(--bs)} CSS token \\
    \code{shop\_name}     & TEXT  & \code{''}            & overrides \code{APP\_NAME} env var \\
    \code{shop\_subtitle} & TEXT  & \code{''}            & overrides \code{APP\_SUBTITLE} env var \\
    \code{imprint\_text}  & TEXT  & \code{''}            & rendered on \route{/impressum} \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection*{\texttt{app\_config}}

Singleton row (\code{id = 1}).  Written via \route{POST /admin/smtp}
and \route{POST /admin/ai-config}.  DB values override environment
variables at runtime.

\begin{table}[H]
  \centering\small
  \begin{tabular}{@{}llll@{}}
    \toprule
    \textbf{Column} & \textbf{Type} & \textbf{Default} & \textbf{Notes} \\
    \midrule
    \code{id}           & INT     & 1        & PK, CHECK (id = 1) \\
    \code{smtp\_host}   & TEXT    & \code{''} & SMTP server hostname \\
    \code{smtp\_port}   & TEXT    & \code{'587'} & \\
    \code{smtp\_from}   & TEXT    & \code{''} & sender address \\
    \code{smtp\_username}& TEXT   & \code{''} & \\
    \code{smtp\_password}& TEXT   & \code{''} & stored in plain text \\
    \code{smtp\_tls}    & BOOLEAN & FALSE    & enable STARTTLS \\
    \code{ai\_provider} & TEXT    & \code{''} & e.g.\ \code{claude}, \code{openai} \\
    \code{ai\_endpoint} & TEXT    & \code{''} & custom API base URL \\
    \code{ai\_api\_key} & TEXT    & \code{''} & stored in plain text \\
    \code{ai\_model}    & TEXT    & \code{''} & model ID string \\
    \bottomrule
  \end{tabular}
\end{table}

% ─────────────────────────────────────────────────────────────
\section{Foreign Key Relationships}
\label{sec:schema-fk}

\begin{figure}[H]
\centering
\begin{tikzpicture}[
  tbl/.style={rectangle, draw=ohc-blue!50, fill=ohc-blue!6,
              rounded corners=3pt, minimum width=3.2cm,
              minimum height=0.75cm, align=center, font=\small\ttfamily},
  fk/.style={->, >=Stealth, gray!70, thick},
  casc/.style={->, >=Stealth, ohc-blue!80, thick, dashed},
  node distance=0.45cm and 1.6cm
]
  % Column 1
  \node[tbl] (users)    {users};
  \node[tbl, below=of users]  (cats)  {categories};
  \node[tbl, below=of cats]   (srcs)  {gitlab\_sources};

  % Column 2
  \node[tbl, right=2.8cm of users]  (proj) {projects};
  \node[tbl, below=of proj]         (prods) {products};
  \node[tbl, below=of prods]        (envs)  {deployment\_environments};

  % Column 3
  \node[tbl, right=2.8cm of proj]   (orders) {orders};
  \node[tbl, below=of orders]       (pe)     {product\_environments};
  \node[tbl, below=of pe]           (pw)     {product\_webhooks};

  % Column 4
  \node[tbl, right=2.8cm of orders] (infra)  {infrastructure\_elements};
  \node[tbl, below=of infra]        (audit)  {audit\_log};

  % FKs (solid = normal, dashed = cascade delete)
  \draw[fk]   (proj)   -- node[above,font=\tiny]{owner}   (users);
  \draw[casc] (prods)  -- node[above,font=\tiny]{cat}      (cats);
  \draw[fk]   (envs)   -- node[above,font=\tiny]{source}   (srcs);
  \draw[casc] (orders) -- node[above,font=\tiny]{proj}     (proj);
  \draw[casc] (orders.west) to[bend right=20] node[below,font=\tiny]{prod} (prods.east);
  \draw[fk]   (orders.west) to[bend right=35] node[below,font=\tiny]{env}  (envs.east);
  \draw[fk]   (orders)      to[bend left=15]  node[above,font=\tiny]{user} (users.east);
  \draw[casc] (pe)     -- node[right,font=\tiny]{prod}    (prods);
  \draw[fk]   (pe)     -- node[above,font=\tiny]{env}     (envs);
  \draw[casc] (pw)     -- node[right,font=\tiny]{prod}    (prods);
  \draw[fk]   (pw)     -- node[above,font=\tiny]{env}     (envs);
  \draw[casc] (infra)  -- node[above,font=\tiny]{proj}    (proj);
  \draw[casc] (infra.west) to[bend left=20] node[above,font=\tiny]{prod} (prods.east);
  \draw[fk]   (audit)  to[bend left=15]    node[left,font=\tiny]{user}  (users.east);
\end{tikzpicture}
\caption{Simplified FK diagram. Dashed arrows = ON DELETE CASCADE; solid arrows = restricted.}
\end{figure}

\notebox{The cascade policy ensures that deleting a \textbf{product},
\textbf{project}, or \textbf{category} automatically removes all
dependent rows (orders, infra elements, translations, etc.) without
requiring explicit cleanup in application code.}

% ─────────────────────────────────────────────────────────────
\section{Indexes}
\label{sec:schema-indexes}

\begin{table}[H]
  \centering
  \caption{Non-primary-key indexes}
  \begin{tabular}{@{}lll@{}}
    \toprule
    \textbf{Index name} & \textbf{Table} & \textbf{Columns} \\
    \midrule
    \code{idx\_products\_category}   & \code{products}               & \code{category\_id} \\
    \code{idx\_orders\_user}         & \code{orders}                 & \code{user\_id} \\
    \code{idx\_orders\_status}       & \code{orders}                 & \code{status} \\
    \code{idx\_orders\_project}      & \code{orders}                 & \code{project\_id} \\
    \code{idx\_infra\_project}       & \code{infrastructure\_elements} & \code{project\_id} \\
    \code{idx\_infra\_status}        & \code{infrastructure\_elements} & \code{status} \\
    \code{idx\_projects\_owner}      & \code{projects}               & \code{owner\_id} \\
    \code{idx\_audit\_user}          & \code{audit\_log}             & \code{user\_id} \\
    \code{idx\_audit\_action}        & \code{audit\_log}             & \code{action} \\
    \code{idx\_parameters\_scope}    & \code{parameters}             & \code{scope, scope\_id, environment\_id} \\
    \code{idx\_product\_webhooks}    & \code{product\_webhooks}      & \code{product\_id, environment\_id, exec\_order} \\
    \bottomrule
  \end{tabular}
\end{table}

% ─────────────────────────────────────────────────────────────
\chapter{Adding a New Feature}
\label{ch:new-feature}

This chapter describes the canonical pattern for adding a feature end-to-end.

\section{Example: Adding a New Admin Page}

\textbf{Goal:} Add an admin page at \route{/admin/widgets} that lists
and creates widgets stored in a new \code{widgets} database table.

\subsection{Step 1: Create the Migration}

Create \file{internal/migrations/010\_widgets.sql}:

\begin{lstlisting}[style=sql]
CREATE TABLE IF NOT EXISTS widgets (
  id   BIGSERIAL PRIMARY KEY,
  name TEXT NOT NULL,
  active BOOLEAN NOT NULL DEFAULT TRUE,
  created_at TIMESTAMPTZ NOT NULL DEFAULT now()
);
\end{lstlisting}

\subsection{Step 2: Add the Model}

In \file{internal/model/model.go}:

\begin{lstlisting}[style=go]
type Widget struct {
    ID        int64
    Name      string
    Active    bool
    CreatedAt time.Time
}
\end{lstlisting}

\subsection{Step 3: Define the Repository Interface}

In \file{internal/repository/repository.go}:

\begin{lstlisting}[style=go]
type WidgetRepository interface {
    FindAll(ctx context.Context) ([]model.Widget, error)
    Create(ctx context.Context, name string) error
    Delete(ctx context.Context, id int64) error
}
\end{lstlisting}

\subsection{Step 4: Implement the Repository}

Create \file{internal/repository/postgres/widget.go}:

\begin{lstlisting}[style=go]
type widgetRepo struct{ pool *pgxpool.Pool }

func NewWidgetRepository(pool *pgxpool.Pool) repository.WidgetRepository {
    return &widgetRepo{pool: pool}
}

func (r *widgetRepo) FindAll(ctx context.Context) ([]model.Widget, error) {
    rows, err := r.pool.Query(ctx,
        `SELECT id, name, active, created_at FROM widgets ORDER BY name`)
    // ... scan rows into []model.Widget
}
\end{lstlisting}

\subsection{Step 5: Add the Handler}

Add to the \code{Handler} struct in \file{routes.go}:
\begin{lstlisting}[style=go]
widgets repository.WidgetRepository
\end{lstlisting}

Add to \code{Deps} struct and wire in \code{New()}.
Add a view struct in \file{internal/view/pages.go}:

\begin{lstlisting}[style=go]
type AdminWidgetsView struct {
    view.PageData
    Widgets []model.Widget
}
\end{lstlisting}

Add handler methods to a new file \file{handler/widgets.go}:

\begin{lstlisting}[style=go]
func (h *Handler) adminWidgets(w http.ResponseWriter, r *http.Request) {
    items, _ := h.widgets.FindAll(r.Context())
    renderTempl(w, r, adminpages.AdminWidgets(view.AdminWidgetsView{
        PageData: h.buildPageData(w, r),
        Widgets:  items,
    }))
}
\end{lstlisting}

Register routes in \code{RegisterRoutes}:
\begin{lstlisting}[style=go]
mux.Handle("GET /admin/widgets",  admin(h.adminWidgets))
mux.Handle("POST /admin/widgets", admin(h.adminWidgetCreate))
\end{lstlisting}

\subsection{Step 6: Create the templ Component}

Create \file{ui/pages/admin/widgets.templ}:

\begin{lstlisting}[style=go]
package admin

import (
    "github.com/Maximilian-Maag/open-hybrid-cloud/src/internal/i18n"
    "github.com/Maximilian-Maag/open-hybrid-cloud/src/internal/view"
    "github.com/Maximilian-Maag/open-hybrid-cloud/src/ui/comp"
)

templ AdminWidgets(vd view.AdminWidgetsView) {
    @comp.Layout(vd.PageData) {
        @comp.PageHeader(i18n.T("admin.widgets", vd.Lang), "/admin")
        @comp.Card() {
            <table class="w-full text-sm">
                <tbody>
                    for _, w := range vd.Widgets {
                        <tr class="hover:bg-slate-50">
                            <td class="px-4 py-3">{ w.Name }</td>
                        </tr>
                    }
                </tbody>
            </table>
        }
    }
}
\end{lstlisting}

Run \code{templ generate ./...} to compile to Go, then \code{go build ./...}
to verify type correctness before running.

\subsection{Step 7: Add i18n Keys}

In \file{internal/i18n/i18n.go}, add the key with all 25 language
translations.

\subsection{Step 8: Wire Up in main.go}

\begin{lstlisting}[style=go]
widgetRepo := pgRepo.NewWidgetRepository(pool)
// ...
h := handler.New(handler.Deps{
    // ...
    Widgets: widgetRepo,
})
\end{lstlisting}

\subsection{Step 9: Test}

Add test stubs in \file{internal/repository/} (or use the real DB in
integration tests). Run:

\begin{lstlisting}[style=bash]
make test
make vet
make lint
\end{lstlisting}

% ─────────────────────────────────────────────────────────────
%  PART V — PROJECT MANAGER GUIDE
% ─────────────────────────────────────────────────────────────
\part{Project Manager \& Product Lifecycle Guide}
\label{part:pm}

% ─────────────────────────────────────────────────────────────
\chapter{Ordering Infrastructure}
\label{ch:ordering}

\section{The Order Lifecycle}

\begin{figure}[H]
\centering
\resizebox{\textwidth}{!}{%
\begin{tikzpicture}[
  state/.style={rectangle, rounded corners=6pt, draw=ohc-blue!60,
                fill=ohc-blue!10, minimum width=3.2cm,
                minimum height=1.0cm, align=center, font=\small},
  arr/.style={->, >=Stealth, thick, gray!70},
  node distance=0.5cm and 1.8cm
]
  \node[state] (placed)   {Order Placed};
  \node[state, right=of placed] (pend) {Pending\\Approval};
  \node[state, right=of pend]  (prov) {Provisioning};
  \node[state, right=of prov]  (done) {Completed};
  \node[state, below=0.8cm of pend] (rej) {Rejected};
  \node[state, below=0.8cm of prov] (fail) {Failed};

  \draw[arr] (placed) -- node[c4label,above]{\scriptsize Admin\\(direct)} (prov);
  \draw[arr] (placed) -- node[c4label,above]{\scriptsize Project Mgr} (pend);
  \draw[arr] (pend)   -- node[c4label,above]{\scriptsize approved} (prov);
  \draw[arr] (pend)   -- node[c4label,right]{\scriptsize rejected} (rej);
  \draw[arr] (prov)   -- node[c4label,above]{\scriptsize pipeline OK} (done);
  \draw[arr] (prov)   -- node[c4label,right]{\scriptsize pipeline fail} (fail);

\end{tikzpicture}}%
\caption{Order lifecycle state machine}
\label{fig:lifecycle}
\end{figure}

\section{Placing an Order}

\begin{enumerate}
  \item Navigate to \textbf{Catalog} and select a product.
  \item Click \textbf{Configure} → select the deployment environment.
  \item Select or create a \textbf{Project}.
  \item Fill in the \textbf{Parameters} (required fields are marked).
  \item Select or confirm the \textbf{Cost Center}.
  \item Click \textbf{Deploy Now}.
\end{enumerate}

As a \role{Project Manager} the order status changes to
\textit{Pending Approval}. An Admin receives an email notification.

As a \role{Admin} the GitLab webhook fires immediately.

\section{Tracking Status}

After placing an order, navigate to \textbf{My Orders → \{order\}}.
The status updates live via HTMX polling every 30 seconds.

\section{Using an Existing Deployment as a Template}

\begin{enumerate}
  \item Open \textbf{Infrastructure}.
  \item Find the resource and click \textbf{Use as Template}.
  \item The order form opens pre-filled with the original parameters.
  \item Modify as needed and submit.
\end{enumerate}

\section{Decommissioning}
\label{sec:decommission}

\begin{enumerate}
  \item Open \textbf{Infrastructure}.
  \item Find the resource and click \textbf{Decommission}.
  \item Confirm the action.
  \item The destroy webhook fires; status changes to
        \textit{Decommissioning}.
  \item On pipeline completion, status becomes \textit{Decommissioned}.
\end{enumerate}

\subsection*{Cascade Decommissioning on Deletion}

Deleting a \textbf{project}, \textbf{product}, or \textbf{category}
automatically triggers decommissioning for all active infrastructure elements
associated with that object before the database record is removed:

\begin{itemize}
  \item \textbf{Project deleted} — all active infrastructure elements of the
    project receive a destroy webhook call.
  \item \textbf{Product deleted} — all active infrastructure elements
    provisioned from that product receive a destroy webhook call.
  \item \textbf{Category deleted} — all active infrastructure elements of every
    product in the category receive a destroy webhook call.
\end{itemize}

Infrastructure already in status \textit{Decommissioning} or
\textit{Decommissioned} is skipped. Dependent database rows (translations,
parameters, environment assignments) are removed automatically via PostgreSQL
\code{ON DELETE CASCADE} constraints after the webhooks have been triggered.

\warnbox{Deleting a project, product, or category is irreversible. All associated
cloud resources will be destroyed by OpenTofu. Verify there are no active
workloads before proceeding.}

% ─────────────────────────────────────────────────────────────
\chapter{Introducing a New Product}
\label{ch:new-product}

This chapter describes the complete process for making a new
infrastructure product available in the webshop. Follow the steps
sequentially.

\section{Overview}

\begin{enumerate}
  \item Plan the product
  \item Prepare the OpenTofu module
  \item Configure the GitLab webhook
  \item Create the product in the Admin UI
  \item Define parameters (import or manual)
  \item Configure deployment environments and pricing
  \item Set up AI translations
  \item Test the full order flow
  \item Publish
\end{enumerate}

\section{Step 1: Plan the Product}

Before touching any UI, answer these questions:

\begin{itemize}
  \item \textbf{What does the product deploy?}
    (e.g. \textit{Managed PostgreSQL VM on Linode})
  \item \textbf{Which OpenTofu module delivers it?}
    (\code{vm-platform}, \code{k8s-platform}, or a new module)
  \item \textbf{In which environments is it available?}
    (e.g. Linode Frankfurt, Linode Amsterdam)
  \item \textbf{What parameters does the user need to provide?}
    (e.g. \code{vm\_label}, \code{instance\_type}, \code{db\_name})
  \item \textbf{What is the base price in EUR per environment?}
  \item \textbf{Who assigns the cost center?} (project / select / overhead)
\end{itemize}

\section{Step 2: Prepare the OpenTofu Module}

If the product uses an existing module (\code{vm-platform} or
\code{k8s-platform}), skip to Step 3. For a new product type:

\begin{enumerate}
  \item Create a new GitLab repository in the \code{open-hybrid-cloud} group.
  \item Add the standard files:
        \file{provider.tf}, \file{backend.tf}, \file{variables.tf},
        \file{main.tf}, \file{outputs.tf}, \file{.gitlab-ci.yml}.
  \item Declare all user-provided parameters as \code{variable} blocks
        in \file{variables.tf} with \code{description}, \code{type},
        and \code{default} where applicable:

\begin{lstlisting}[style=hcl]
variable "db_name" {
  description = "Name of the PostgreSQL database to create."
  type        = string
}

variable "db_size_gb" {
  description = "Database volume size in GB."
  type        = number
  default     = 20
}
\end{lstlisting}

  \item Test the module locally:
\begin{lstlisting}[style=bash]
tofu init -backend-config="address=..." \
          -backend-config="username=..." \
          -backend-config="password=..."
tofu plan -var="linode_token=$TOKEN" \
          -var="db_name=test" \
          -var="db_size_gb=20"
tofu apply
tofu destroy
\end{lstlisting}
  \item Commit and push to the \code{main} branch.
\end{enumerate}

\section{Step 3: Configure the GitLab Webhook}

In the GitLab repository:

\begin{enumerate}
  \item Go to \textbf{Settings → CI/CD → Pipeline trigger tokens}.
  \item Click \textbf{Add new token} and give it a descriptive name
        (e.g. \textit{webshop-prod}).
  \item Note the \textbf{trigger URL} and \textbf{token}.
\end{enumerate}

The trigger URL has the form:
\begin{lstlisting}[style=bash]
https://gitlab.example.com/api/v4/projects/<PROJECT_ID>/ref/main/trigger/pipeline
\end{lstlisting}

\section{Step 4: Create a Category (if needed)}

Under \textbf{Administration → Categories}:

\begin{enumerate}
  \item Click \textbf{New Category}.
  \item Enter a \textbf{Name}.
  \item Optionally assign a \textbf{Category Parameter Set} (see Step 5).
  \item Save.
\end{enumerate}

\section{Step 5: Create the Product}
\label{sec:step5}

Under \textbf{Administration → Products → New}:

\subsection{Basic Information}

\begin{enumerate}
  \item Select the \textbf{Category}.
  \item Enter the product \textbf{Name} in the primary language.
  \item Enter a detailed \textbf{Description} in the primary language.
  \item Upload a product \textbf{Image} (PNG or JPEG, max 10 MB).
  \item Click \textbf{Save \& Continue}.
\end{enumerate}

\subsection{Parameters}

Choose one of two import methods:

\textbf{Option A — Import from \texttt{variables.tf}} (recommended):

\begin{enumerate}
  \item Click \textbf{Browse Repository}.
  \item Select the \textbf{GitLab Source} and the repository.
  \item Select the branch (\code{main}) and navigate to
        \file{variables.tf}.
  \item Click \textbf{Import Parameters}.
  \item The webshop parses the HCL and creates parameter records for
        each variable. Review and adjust:
        \begin{itemize}
          \item \textbf{Required} — must the user fill this in?
          \item \textbf{Sensitive} — should the value be masked in
                the UI and audit log?
          \item \textbf{Default value} — pre-fill the order form.
          \item \textbf{Type} — text, number, boolean, or dropdown.
        \end{itemize}
\end{enumerate}

\textbf{Option B — Manual entry}:

Click \textbf{Add Parameter} and fill in each field manually.

\notebox{Parameters whose names match OpenTofu variable names
(e.g. \code{instance\_type}) are passed to the webhook as
\code{TF\_VAR\_instance\_type}. The name in the webshop must match
the \code{variable} block name in \file{variables.tf} exactly.}

\subsection{Deployment Environments}

\begin{enumerate}
  \item Click \textbf{Add Environment}.
  \item Select an environment from the dropdown (must be pre-configured
        under Administration → Environments).
  \item Enter the \textbf{Price} in the base currency.
  \item For the webhook, either:
        \begin{itemize}
          \item Use the environment's default webhook URL, or
          \item Enter a product-specific webhook URL and token.
        \end{itemize}
  \item Configure the \textbf{Cost Center Mode}:
        \begin{description}
          \item[Project] Cost center inherited from the project.
          \item[Select] Orderer selects from the cost center list.
          \item[Overhead] Always assigns a fixed cost center.
        \end{description}
  \item Repeat for each environment.
\end{enumerate}

\subsection{Multiple Webhooks (Pipeline Arrays)}

A single product-environment combination can have multiple webhooks
executed in order (e.g. first provision the VM, then configure DNS,
then register in Vault). Under the webhook section:

\begin{enumerate}
  \item Click \textbf{Add Webhook}.
  \item Enter URL, token, and \textbf{Execution Order} (1, 2, 3 …).
  \item Webhooks are triggered sequentially in ascending order.
\end{enumerate}

\section{Step 6: Configure AI Translation}

\begin{enumerate}
  \item Ensure an AI provider is configured (Chapter~\ref{ch:sysconfig}).
  \item Open the product in \textbf{Administration → Products}.
  \item Click \textbf{Generate AI Translation}.
  \item Review the generated translations for all 25 languages.
  \item Edit any that require adjustment.
  \item Save.
\end{enumerate}

\tipbox{Generate translations early in the process. The AI translates
both the product name and description. Individual translations can
be re-generated for specific languages by editing the translation
tab directly.}

\section{Step 7: Global and Category Parameter Sets}

\textbf{Global parameters} (under \textbf{Administration → Global
Parameters}) apply to every order regardless of product. Use them for
organization-wide fields such as a cost center code or project tag that
must always be captured.

\textbf{Category parameters} (under \textbf{Administration → Categories
→ \{category\} → Parameters}) apply to all products within a category.
Use them to avoid repeating parameters shared by related products
(e.g. all VM products share a \code{region} parameter).

\textbf{Parameter hierarchy} (applied in this order on the order form):
\begin{enumerate}
  \item Global parameters
  \item Category parameters
  \item Product parameters
  \item Environment-specific parameters (override per-environment)
\end{enumerate}

\section{Step 8: Test the Full Order Flow}

\begin{enumerate}
  \item Log in as a \role{Admin} (Admins trigger webhooks directly).
  \item Navigate to \textbf{Catalog} and find the new product.
  \item Click \textbf{Configure}, fill in test parameters, and
        click \textbf{Deploy Now}.
  \item Monitor the order under \textbf{My Orders} — the status should
        progress from \textit{Provisioning} to \textit{Completed}.
  \item Verify the infrastructure was created in the Linode Cloud
        Manager.
  \item Test the email notification (check the admin email inbox).
  \item Test the \textbf{Decommission} flow:
        \begin{itemize}
          \item Open \textbf{Infrastructure}.
          \item Click \textbf{Decommission} on the test resource.
          \item Verify the destroy pipeline runs and the resource
                disappears from the Linode Cloud Manager.
        \end{itemize}
\end{enumerate}

\warnbox{Always test decommission in a non-production environment first.
A destroy pipeline permanently deletes cloud resources and their data.}

\section{Step 9: Test with a Project Manager Account}

\begin{enumerate}
  \item Log in (or create a test account) as a \role{Project Manager}.
  \item Place an order for the new product.
  \item Verify the order shows \textit{Pending Approval}.
  \item Switch to the \role{Admin} account.
  \item Approve the order under \textbf{Approvals}.
  \item Verify the webhook fires and provisioning completes.
  \item Verify the Project Manager receives the confirmation email.
\end{enumerate}

\section{Step 10: Product is Live}

Once testing passes:
\begin{itemize}
  \item The product is immediately visible in the catalog.
  \item No deployment or restart of the webshop is required.
  \item Announce the new product to users via the notification service
        or the shop's subtitle/branding.
\end{itemize}

% ─────────────────────────────────────────────────────────────
\chapter{Project Management}
\label{ch:projects}

\section{Projects}

A \term{project} is a container for related infrastructure orders. Every
order must be associated with a project. Projects have:
\begin{itemize}
  \item A \textbf{Name} and optional \textbf{Description}.
  \item An optional \textbf{Cost Center} (used when cost center mode
        is \textit{Project}).
  \item An owner (the user who created it).
\end{itemize}

\role{Project Managers} see only their own projects.
\role{Admins} and \role{Root users} see all projects.

\section{Infrastructure Overview}
\label{sec:infra-overview}

The \textbf{Infrastructure} page shows all deployed resources grouped by
project and environment. Each resource shows:
\begin{itemize}
  \item Product name and environment.
  \item Deployment date and current status.
  \item Key parameters (e.g. VM label, cluster name).
  \item Buttons: \textbf{Use as Template}, \textbf{Decommission}.
\end{itemize}

\section{Cost Center Assignment}

Cost centers are maintained under \textbf{Administration → Cost Centers}.
The three assignment modes give fine-grained control over who can
allocate costs:

\begin{description}
  \item[Project] No user input; cost center comes from the project.
        Use for products where cost is always allocated to the project
        budget.
  \item[Select] Orderer picks from the cost center list. Use when
        individual orders can span cost centers.
  \item[Overhead] Always assigns a fixed cost center regardless of
        order. Use for shared services (monitoring, DNS).
\end{description}

% ─────────────────────────────────────────────────────────────
%  APPENDICES
% ─────────────────────────────────────────────────────────────
\appendix

\chapter{Supported Languages}
\label{app:languages}

The following 25 languages are supported in the UI and for AI product
translation:

\begin{longtable}{@{}lll@{}}
  \toprule
  \textbf{Code} & \textbf{Language} & \textbf{Native name} \\
  \midrule
  \endhead
  \code{de} & German     & Deutsch \\
  \code{en} & English    & English \\
  \code{fr} & French     & Fran\c{c}ais \\
  \code{it} & Italian    & Italiano \\
  \code{es} & Spanish    & Espa\~{n}ol \\
  \code{pt} & Portuguese & Portugu\^{e}s \\
  \code{nl} & Dutch      & Nederlands \\
  \code{pl} & Polish     & Polski \\
  \code{cs} & Czech      & \v{C}e\v{s}tina \\
  \code{sk} & Slovak     & Sloven\v{c}ina \\
  \code{hu} & Hungarian  & Magyar \\
  \code{ro} & Romanian   & Rom\^{a}n\u{a} \\
  \code{bg} & Bulgarian  & Balgarski (Cyrillic) \\
  \code{hr} & Croatian   & Hrvatski \\
  \code{sl} & Slovenian  & Sloven\v{s}\v{c}ina \\
  \code{et} & Estonian   & Eesti \\
  \code{lv} & Latvian    & Latvie\v{s}u \\
  \code{lt} & Lithuanian & Lietuvi\k{u} \\
  \code{fi} & Finnish    & Suomi \\
  \code{sv} & Swedish    & Svenska \\
  \code{da} & Danish     & Dansk \\
  \code{el} & Greek      & Ellinika (Greek script) \\
  \code{mt} & Maltese    & Malti \\
  \code{ru} & Russian    & Russkij (Cyrillic) \\
  \code{uk} & Ukrainian  & Ukrayinska (Cyrillic) \\
  \bottomrule
  \caption{Supported language codes}
  \label{tab:languages}
\end{longtable}

\chapter{Environment Variable Reference}
\label{app:envvars}

\begin{longtable}{@{}L{4.5cm}L{7.5cm}l@{}}
  \toprule
  \textbf{Variable} & \textbf{Description} & \textbf{Required} \\
  \midrule
  \endhead
  \env{DATABASE\_URL}         & PostgreSQL connection string (DSN)          & Yes \\
  \env{SESSION\_KEY}          & 32-byte hex key for session encryption       & Yes \\
  \env{ADMIN\_EMAIL}          & Email of the initial Root account   & Yes \\
  \env{ADMIN\_PASSWORD}       & Password of the initial admin account        & Yes \\
  \env{BASE\_URL}             & Public base URL (e.g. \code{https://shop.example.com}) & Yes \\
  \env{PORT}                  & HTTP listen port (default: \code{8080})      & No  \\
  \env{OIDC\_CLIENT\_ID}      & Entra ID application (client) ID             & No  \\
  \env{OIDC\_CLIENT\_SECRET}  & Entra ID client secret                       & No  \\
  \env{OIDC\_ISSUER}          & OIDC issuer URL (\code{https://login.microsoft...}) & No  \\
  \env{SMTP\_HOST}            & SMTP server hostname                         & No  \\
  \env{SMTP\_PORT}            & SMTP port (default: \code{587})              & No  \\
  \env{SMTP\_FROM}            & Sender email address                         & No  \\
  \env{SMTP\_USERNAME}        & SMTP authentication username                 & No  \\
  \env{SMTP\_PASSWORD}        & SMTP authentication password                 & No  \\
  \env{SMTP\_TLS}             & \code{true} to use TLS/SSL                   & No  \\
  \env{AI\_PROVIDER}          & AI translation provider at startup           & No  \\
  \env{AI\_ENDPOINT}          & AI API endpoint URL                          & No  \\
  \env{AI\_API\_KEY}          & AI API key                                   & No  \\
  \env{AI\_MODEL}             & AI model name                                & No  \\
  \env{EXCHANGE\_RATE\_KEY}   & Exchange rate API key                        & No  \\
  \bottomrule
  \caption{Environment variable reference}
  \label{tab:envvars}
\end{longtable}

\chapter{OpenTofu Module Variable Reference}
\label{app:tofu-vars}
\footnotesize

\section{network-core Variables}

\begin{longtable}{@{}L{4.2cm}lL{5.3cm}l@{}}
  \toprule
  \textbf{Variable} & \textbf{Type} & \textbf{Description} & \textbf{Default} \\
  \midrule
  \endhead
  \code{linode\_token}      & string  & Linode API token (sensitive)    & — \\
  \code{region}             & string  & Linode region                   & \code{eu-central} \\
  \code{vpc\_label}         & string  & VPC label                       & \code{ohc-vpc-prod} \\
  \code{vpc\_description}   & string  & VPC description                 & (see defaults) \\
  \code{subnets}            & map(obj)& Subnet map (label→cidr)         & app + mgmt \\
  \code{firewall\_inbound\_rules} & list(obj) & Inbound firewall rules  & SSH + ICMP \\
  \code{dns\_domain}        & string  & DNS zone domain (empty=none)    & \code{""} \\
  \code{tags}               & list    & Resource tags                   & \code{["infra","network-core"]} \\
  \bottomrule
  \caption{network-core variables}
\end{longtable}

\section{vm-platform Variables}

\begin{longtable}{@{}L{4.2cm}lL{5.3cm}l@{}}
  \toprule
  \textbf{Variable} & \textbf{Type} & \textbf{Description} & \textbf{Default} \\
  \midrule
  \endhead
  \code{linode\_token}     & string & Linode API token (sensitive)   & — \\
  \code{vm\_label}         & string & Unique VM label (state name)   & — \\
  \code{region}            & string & Linode region                  & \code{eu-central} \\
  \code{vpc\_id}           & number & VPC ID from network-core        & — \\
  \code{subnet\_id}        & number & Subnet ID from network-core     & — \\
  \code{firewall\_id}      & number & Base firewall ID                & — \\
  \code{instance\_type}    & string & Linode plan                    & \code{g6-standard-2} \\
  \code{image}             & string & Boot image                     & \code{linode/debian12} \\
  \code{root\_pass}        & string & Root password (sensitive)      & — \\
  \code{ssh\_keys}         & list   & Authorized SSH keys            & \code{[]} \\
  \code{volume\_size\_gb}  & number & Block storage size (0=none)    & \code{0} \\
  \code{additional\_inbound\_rules} & list(obj) & Extra firewall rules & \code{[]} \\
  \code{dns\_zone\_id}     & number & DNS zone ID (null=none)        & \code{null} \\
  \code{dns\_hostname}     & string & A record hostname              & \code{""} \\
  \code{tags}              & list   & Resource tags                  & \code{["infra","vm"]} \\
  \bottomrule
  \caption{vm-platform variables}
\end{longtable}

\section{k8s-platform Variables}

\begin{longtable}{@{}L{4.2cm}lL{5.3cm}l@{}}
  \toprule
  \textbf{Variable} & \textbf{Type} & \textbf{Description} & \textbf{Default} \\
  \midrule
  \endhead
  \code{linode\_token}       & string    & Linode API token (sensitive) & — \\
  \code{cluster\_label}      & string    & Unique cluster label         & — \\
  \code{region}              & string    & Linode region                & \code{eu-central} \\
  \code{kubernetes\_version} & string    & K8s version                  & \code{1.31} \\
  \code{vpc\_id}             & number    & VPC ID                       & — \\
  \code{subnet\_id}          & number    & Subnet ID                    & — \\
  \code{node\_pools}         & list(obj) & Node pool configurations     & 1× g6-standard-2 \\
  \code{additional\_inbound\_rules} & list(obj) & Extra firewall rules & \code{[]} \\
  \code{dns\_zone\_id}       & number    & DNS zone ID (null=none)      & \code{null} \\
  \code{dns\_hostname}       & string    & A record hostname            & \code{""} \\
  \code{tags}                & list      & Resource tags                & \code{["infra","k8s"]} \\
  \bottomrule
  \caption{k8s-platform variables}
\end{longtable}

\section{shared-services Variables}

\begin{longtable}{@{}L{4.2cm}lL{5.3cm}l@{}}
  \toprule
  \textbf{Variable} & \textbf{Type} & \textbf{Description} & \textbf{Default} \\
  \midrule
  \endhead
  \code{linode\_token}          & string & Linode API token (sensitive)        & — \\
  \code{region}                 & string & Linode region                       & \code{eu-central} \\
  \code{gitlab\_label}          & string & GitLab CE Linode label              & \code{ohc-gitlab} \\
  \code{gitlab\_instance\_type} & string & Linode plan for GitLab CE           & \code{g6-standard-4} \\
  \code{vault\_label}           & string & Vault Linode label                  & \code{ohc-vault} \\
  \code{vault\_instance\_type}  & string & Linode plan for Vault               & \code{g6-standard-2} \\
  \code{image}                  & string & Boot image                         & \code{linode/debian12} \\
  \code{root\_pass}             & string & Root password (sensitive)           & — \\
  \code{ssh\_keys}              & list   & Authorized SSH keys                 & \code{[]} \\
  \code{vpc\_id}                & number & VPC ID from network-core            & — \\
  \code{subnet\_id}             & number & Subnet ID from network-core         & — \\
  \code{allowed\_admin\_ipv4}   & list   & IPv4 CIDRs for SSH \& Vault admin   & \code{["0.0.0.0/0"]} \\
  \code{tags}                   & list   & Resource tags                       & \code{["infra","shared"]} \\
  \bottomrule
  \caption{shared-services variables}
  \label{tab:vars-shared}
\end{longtable}

\section{observability Variables}

\begin{longtable}{@{}L{4.2cm}lL{5.3cm}l@{}}
  \toprule
  \textbf{Variable} & \textbf{Type} & \textbf{Description} & \textbf{Default} \\
  \midrule
  \endhead
  \code{linode\_token}           & string & Linode API token (sensitive)      & — \\
  \code{region}                  & string & Linode region                     & \code{eu-central} \\
  \code{obs\_label}              & string & Linode instance label             & \code{ohc-obs} \\
  \code{instance\_type}          & string & Linode plan                       & \code{g6-standard-2} \\
  \code{image}                   & string & Boot image                        & \code{linode/debian12} \\
  \code{root\_pass}              & string & Root password (sensitive)         & — \\
  \code{ssh\_keys}               & list   & Authorized SSH keys               & \code{[]} \\
  \code{vpc\_id}                 & number & VPC ID from network-core          & — \\
  \code{subnet\_id}              & number & Subnet ID from network-core       & — \\
  \code{volume\_size\_gb}        & number & Block storage size in GiB         & \code{200} \\
  \code{grafana\_port}           & number & Grafana HTTP port                 & \code{3000} \\
  \code{allowed\_grafana\_ipv4}  & list   & IPv4 CIDRs for Grafana access     & \code{["0.0.0.0/0"]} \\
  \code{tags}                    & list   & Resource tags                     & \code{["infra","obs"]} \\
  \bottomrule
  \caption{observability variables}
  \label{tab:vars-obs}
\end{longtable}

\chapter{HTTP Route Reference}
\label{app:routes}

All routes are registered in \code{src/internal/handler/routes.go}.
The \textbf{Role} column uses the following abbreviations:

\begin{itemize}
  \item \textbf{public} — no authentication required
  \item \textbf{auth} — any authenticated user
  \item \textbf{admin} — role \code{admin} or higher
  \item \textbf{root} — role \code{root} only
\end{itemize}

\footnotesize
\begin{longtable}{@{}lL{7.8cm}L{4.5cm}l@{}}
  \toprule
  \textbf{Method} & \textbf{Path} & \textbf{Description} & \textbf{Role} \\
  \midrule
  \endhead

  \multicolumn{4}{@{}l}{\textit{Authentication}} \\[2pt]
  GET  & \code{/login}                                              & Login page                              & public \\
  POST & \code{/login}                                              & Submit credentials                      & public \\
  GET  & \code{/auth/callback}                                      & OIDC / Entra ID callback                & public \\
  POST & \code{/logout}                                             & Destroy session                         & auth \\
  POST & \code{/lang}                                               & Switch UI language                      & auth \\[6pt]

  \multicolumn{4}{@{}l}{\textit{General (any authenticated user)}} \\[2pt]
  GET  & \code{/}                                                   & Home / dashboard                        & auth \\
  GET  & \code{/catalog}                                            & Product catalog                         & auth \\
  GET  & \code{/catalog/\{id\}}                                     & Product detail page                     & auth \\
  GET  & \code{/products/\{id\}/image}                              & Serve product image                     & auth \\
  GET  & \code{/branding/logo}                                      & Serve shop logo                         & auth \\
  GET  & \code{/impressum}                                          & Imprint page                            & auth \\
  GET  & \code{/settings/profile}                                   & Profile \& password change              & auth \\
  POST & \code{/settings/profile}                                   & Save profile / new password             & auth \\[6pt]

  \multicolumn{4}{@{}l}{\textit{Orders}} \\[2pt]
  GET  & \code{/orders}                                             & My orders list                          & auth \\
  GET  & \code{/orders/new}                                         & New order form                          & auth \\
  POST & \code{/orders/new}                                         & Submit order                            & auth \\
  GET  & \code{/orders/\{id\}}                                      & Order detail / status                   & auth \\[6pt]

  \multicolumn{4}{@{}l}{\textit{Projects}} \\[2pt]
  GET  & \code{/projects}                                           & Projects list                           & auth \\
  GET  & \code{/projects/new}                                       & New project form                        & auth \\
  POST & \code{/projects/new}                                       & Create project                          & auth \\
  GET  & \code{/projects/\{id\}}                                    & Project detail                          & auth \\
  POST & \code{/projects/\{id\}}                                    & Update project                          & auth \\
  POST & \code{/projects/\{id\}/delete}                             & Delete project                          & auth \\[6pt]

  \multicolumn{4}{@{}l}{\textit{Infrastructure}} \\[2pt]
  GET  & \code{/infrastructure}                                     & Infrastructure overview                 & auth \\
  POST & \code{/infrastructure/\{id\}/decommission}                 & Trigger decommissioning                 & auth \\[6pt]

  \multicolumn{4}{@{}l}{\textit{Approvals \& Audit (role: admin)}} \\[2pt]
  GET  & \code{/approvals}                                          & Approval queue                          & admin \\
  POST & \code{/approvals/\{id\}/approve}                           & Approve order                           & admin \\
  POST & \code{/approvals/\{id\}/reject}                            & Reject order with note                  & admin \\
  GET  & \code{/audit}                                              & Audit log viewer                        & admin \\
  GET  & \code{/audit/export}                                       & Export audit log (PDF)                  & admin \\[6pt]

  \multicolumn{4}{@{}l}{\textit{Admin — Categories (role: shop\_admin)}} \\[2pt]
  GET  & \code{/admin}                                              & Admin dashboard                         & shop\_admin \\
  GET  & \code{/admin/categories}                                   & Category list                           & shop\_admin \\
  POST & \code{/admin/categories}                                   & Create category                         & shop\_admin \\
  POST & \code{/admin/categories/\{id\}/delete}                     & Delete category                         & shop\_admin \\
  GET  & \code{/admin/categories/\{id\}/parameters}                 & Category-level parameters               & shop\_admin \\
  POST & \code{/admin/categories/\{id\}/parameters}                 & Add category parameter                  & shop\_admin \\
  POST & \code{/admin/categories/\{id\}/parameters/\{pid\}/delete}  & Delete category parameter               & shop\_admin \\[6pt]

  \multicolumn{4}{@{}l}{\textit{Admin — Products (role: shop\_admin)}} \\[2pt]
  GET  & \code{/admin/products}                                     & Product list                            & shop\_admin \\
  GET  & \code{/admin/products/new}                                 & New product form                        & shop\_admin \\
  POST & \code{/admin/products/new}                                 & Create product                          & shop\_admin \\
  GET  & \code{/admin/products/\{id\}}                              & Edit product                            & shop\_admin \\
  POST & \code{/admin/products/\{id\}}                              & Update product                          & shop\_admin \\
  POST & \code{/admin/products/\{id\}/delete}                       & Delete product                          & shop\_admin \\
  POST & \code{/admin/products/\{id\}/translate}                    & Trigger AI translation                  & shop\_admin \\
  GET  & \code{/admin/products/\{id\}/image}                        & Image upload page                       & shop\_admin \\
  POST & \code{/admin/products/\{id\}/image}                        & Upload product image                    & shop\_admin \\
  POST & \code{/admin/products/\{id\}/environments}                 & Link product to environment             & shop\_admin \\
  POST & \code{/admin/products/\{id\}/parameters}                   & Add product parameter                   & shop\_admin \\
  POST & \code{/admin/products/\{id\}/parameters/delete-all}        & Delete all product parameters           & shop\_admin \\
  POST & \code{/admin/products/\{id\}/parameters/\{pid\}/delete}    & Delete single product parameter         & shop\_admin \\
  POST & \code{/admin/products/\{id\}/webhooks}                     & Add product webhook                     & shop\_admin \\
  POST & \code{/admin/products/\{id\}/webhooks/\{wid\}/delete}      & Delete product webhook                  & shop\_admin \\[6pt]

  \multicolumn{4}{@{}l}{\textit{Admin — Environments, Sources, Cost Centers (role: shop\_admin)}} \\[2pt]
  GET  & \code{/admin/environments}                                 & Deployment environment list             & shop\_admin \\
  POST & \code{/admin/environments}                                 & Create environment                      & shop\_admin \\
  POST & \code{/admin/environments/\{id\}/delete}                   & Delete environment                      & shop\_admin \\
  GET  & \code{/admin/sources}                                      & GitLab sources list                     & shop\_admin \\
  POST & \code{/admin/sources}                                      & Create GitLab source                    & shop\_admin \\
  POST & \code{/admin/sources/\{id\}/delete}                        & Delete GitLab source                    & shop\_admin \\
  GET  & \code{/admin/costcenters}                                  & Cost center list                        & shop\_admin \\
  POST & \code{/admin/costcenters}                                  & Create cost center                      & shop\_admin \\
  POST & \code{/admin/costcenters/\{id\}/delete}                    & Delete cost center                      & shop\_admin \\[6pt]

  \multicolumn{4}{@{}l}{\textit{Admin — Users (role: shop\_admin)}} \\[2pt]
  GET  & \code{/admin/users}                                        & User list                               & shop\_admin \\
  POST & \code{/admin/users}                                        & Create user                             & shop\_admin \\
  GET  & \code{/admin/users/\{id\}/edit}                            & Edit user form                          & shop\_admin \\
  POST & \code{/admin/users/\{id\}/edit}                            & Save user changes                       & shop\_admin \\
  POST & \code{/admin/users/\{id\}/deactivate}                      & Deactivate user                         & shop\_admin \\
  POST & \code{/admin/users/\{id\}/delete}                          & Delete user                             & shop\_admin \\[6pt]

  \multicolumn{4}{@{}l}{\textit{Admin — Parameters, Currencies, GitLab (role: shop\_admin)}} \\[2pt]
  GET  & \code{/admin/parameters}                                   & Global parameter list                   & shop\_admin \\
  POST & \code{/admin/parameters}                                   & Create global parameter                 & shop\_admin \\
  POST & \code{/admin/parameters/\{id\}/delete}                     & Delete global parameter                 & shop\_admin \\
  GET  & \code{/admin/currencies}                                   & Exchange rate management                & shop\_admin \\
  POST & \code{/admin/currencies/refresh}                           & Refresh exchange rates                  & shop\_admin \\
  GET  & \code{/admin/gitlab/projects}                              & Browse GitLab projects (AJAX)           & shop\_admin \\
  GET  & \code{/admin/gitlab/branches}                              & Browse GitLab branches (AJAX)           & shop\_admin \\
  GET  & \code{/admin/gitlab/files}                                 & Browse GitLab files (AJAX)              & shop\_admin \\
  POST & \code{/admin/gitlab/import-vars}                           & Import variables from \code{.tf} file   & shop\_admin \\[6pt]

  \multicolumn{4}{@{}l}{\textit{Admin — Configuration (role: shop\_admin)}} \\[2pt]
  GET  & \code{/admin/smtp}                                         & SMTP configuration                      & shop\_admin \\
  POST & \code{/admin/smtp}                                         & Save SMTP settings                      & shop\_admin \\
  GET  & \code{/admin/ai-config}                                    & AI translation configuration            & shop\_admin \\
  POST & \code{/admin/ai-config}                                    & Save AI configuration                   & shop\_admin \\
  GET  & \code{/admin/branding}                                     & Shop branding                           & shop\_admin \\
  POST & \code{/admin/branding}                                     & Save branding settings                  & shop\_admin \\
  \bottomrule
  \caption{Complete HTTP route reference}
  \label{tab:routes}
\end{longtable}

\chapter{Requirements Traceability Matrix}
\label{app:rtm}

The following table maps each functional and non-functional requirement
to the implementation location and the handbook section that describes
it.

\begin{landscape}
\begin{longtable}{@{}lL{5.5cm}L{9.0cm}l@{}}
  \toprule
  \textbf{ID} & \textbf{Requirement} & \textbf{Implementation} & \textbf{Section} \\
  \midrule
  \endhead
  FA-01 & User authentication (local + SSO) &
    \file{internal/service/impl/user.go}, \file{internal/handler/auth.go} &
    \S\ref{ch:users} \\
  FA-02 & Role-based access control (admin, root, project\_leader) &
    \file{internal/middleware/auth.go}, \file{internal/model/user.go} &
    \S\ref{ch:users} \\
  FA-03 & Product catalog with categories &
    \file{internal/handler/catalog.go} &
    \S\ref{ch:ordering} \\
  FA-04 & Configurable product parameters &
    \file{internal/model/parameter.go}, admin UI &
    \S\ref{sec:step5} \\
  FA-05 & Shopping-cart order flow &
    \file{internal/handler/order.go} &
    \S\ref{ch:ordering} \\
  FA-06 & Order approval workflow &
    \file{internal/handler/approval.go} &
    \S\ref{ch:ordering} \\
  FA-07 & GitLab webhook trigger &
    \file{internal/service/impl/pipeline.go} &
    \S\ref{sec:webhook} \\
  FA-08 & Pipeline status polling &
    \file{internal/polling/}, \file{internal/service/impl/pipeline.go} &
    \S\ref{sec:webhook} \\
  FA-09 & Infrastructure overview &
    \file{internal/handler/infrastructure.go} &
    \S\ref{sec:infra-overview} \\
  FA-10 & Decommission (destroy) flow &
    \file{internal/handler/infrastructure.go} &
    \S\ref{sec:decommission} \\
  FA-09.5--9.8 & Cascade decommission on project/product/category delete &
    \file{internal/service/impl/infrastructure.go} &
    \S\ref{sec:decommission} \\
  FA-11 & Audit log &
    \file{internal/audit/}, \file{internal/handler/audit.go} &
    \S\ref{ch:audit} \\
  FA-12 & AI-powered product translation &
    \file{internal/service/impl/translation.go} &
    \S\ref{sec:aitranslation} \\
  FA-13 & Multi-currency support &
    \file{internal/service/impl/currency.go} &
    \S\ref{sec:currencies} \\
  FA-14 & Branding configuration &
    \file{internal/handler/admin.go}, \file{internal/model/branding.go} &
    \S\ref{sec:branding} \\
  \midrule
  NFA-01.1 & Docker deployment &
    \file{Dockerfile}, \file{infra/docker-host/} &
    \S\ref{sec:docker-deploy} \\
  NFA-01.2 & Kubernetes deployment &
    \file{infra/helm/open-hybrid-cloud/} manifests &
    \S\ref{sec:k8s-deploy} \\
  NFA-01.3 & Single binary (embed.FS) &
    \file{cmd/server/main.go}, \code{//go:embed} directives &
    \S\ref{ch:design} \\
  NFA-01.4 & Database migrations at startup &
    \file{cmd/migrate/main.go}, \file{internal/migrations/} &
    \S\ref{sec:dbmigrations} \\
  NFA-02.1 & HTTPS enforcement &
    Nginx config (reverse proxy, TLS termination) &
    \S\ref{sec:docker-deploy} \\
  NFA-02.2 & Secure session cookies &
    \file{internal/session/}, AES-GCM encrypted HttpOnly cookies &
    \S\ref{ch:design} \\
  NFA-02.3 & bcrypt password hashing &
    \file{internal/service/impl/user.go} &
    \S\ref{ch:design} \\
  NFA-02.4 & Role-enforced routes &
    \file{internal/middleware/auth.go} &
    \S\ref{ch:users} \\
  NFA-03 & 25-language i18n &
    \file{internal/i18n/i18n.go} &
    \S\ref{app:languages} \\
  NFA-04 & Audit trail for all state changes &
    \file{internal/audit/service.go} &
    \S\ref{ch:audit} \\
  \bottomrule
  \caption{Requirements traceability matrix}
  \label{tab:rtm}
\end{longtable}
\end{landscape}

\chapter{Compiling This Handbook}
\label{app:compile}

The handbook source is at \file{docs/handbook.tex}. Compile with:

\begin{lstlisting}[style=bash]
# From the repo root
make docs

# Or manually (run twice for ToC/references)
cd docs
pdflatex handbook.tex
pdflatex handbook.tex
\end{lstlisting}

\textbf{Required LaTeX packages:} \code{lmodern}, \code{geometry},
\code{fancyhdr}, \code{xcolor}, \code{tikz}, \code{pgf},
\code{booktabs}, \code{longtable}, \code{tabularx}, \code{listings},
\code{tcolorbox}, \code{hyperref}, \code{enumitem}, \code{float},
\code{caption}, \code{graphicx}, \code{microtype}, \code{parskip},
\code{pdflscape}, \code{pifont}.

All packages are available in TeX Live 2023+ and MiKTeX 23+.

\end{document}
